\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{http://www.cmara.org}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge September 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA September 2016 business meeting was called to order on September 15, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:10 PM.

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

\subsection{Guests \& Visitors}
\texttt{K1BML},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA3RLZ},
\texttt{KB1OKF},
\texttt{KB1VXY},
\texttt{KC1CAR},
\texttt{KC1DQT},
\texttt{KC1ETB},
\texttt{KC1FDQ},
\texttt{KC1FPA},
\texttt{KC1GBK},
\texttt{KC1SGT},
\texttt{KM1D},
\texttt{N1FSK},
\texttt{N1HTB},
\texttt{N1KWX},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1IKE},
\texttt{W1PA},
\texttt{W1RJZ},
\texttt{W1WER},
\texttt{W3DEC},
\texttt{WA1JXR},
\texttt{WA1MDD},
\texttt{WI1Y},
\texttt{WK1H}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}

The secretary report for June has been tabled until the October meeting.

\newpage
\subsection{Treasurer's Report}

The treasurer's report for June has been tabled until the October meeting.

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

The US has recently published that there are 740K ham operators, and contrary to common belief, the number of hams is still increasing. Region 1 (New England) is the 10\textsuperscript{th} fastest growing region.

\subsubsection{Repeater Trustees Report}

\begin{enumerate}
\item There is no new business to report.
\item Before the summer meeting break, the club requested that Greg (\texttt{WA1JXR}) look into alternatives regarding the antenna on the \texttt{W1BIM} repeater. Greg was unable to get a hold of Eric and/or Mike, but he will follow up with Eric.
\end{enumerate}

\subsubsection{Field Day Committee Report}
Gerry (\texttt{W1GD}) prepared a quick presentation on the outcome of the CMARA participation in the 2016 ARRL Field Day.

\begin{enumerate}
\item A total of 36 members and a handful of guests showed up. We had 19 operators active that weekend.
\item We used \texttt{N1MM+} with a new network and it ended up working well.
\item We recorded 1604 contacts, 1100 of those were CW.
\item We did lose some bonus points because the location was not a public place, and thus we couldn't invite the public or officials.
\item The count of QSOs was up from last year (2015), likely due to the better weather allowing for longer operating times.
\item This (2016) was our second best year since 2009.
\item Gerry (\texttt{W1GD}) wants to assemble a better, more complete presentation around January when we're getting ready for next year.
\item There was a question about the generators causing interference. Gerry (\texttt{W1GD}) has used those generators before and found grounding them helped, but that didn't seem to solve the issue during field day. It's possible our interference was due to something nearby.
\end{enumerate}

\section{Old Business}

There was no old business tabled.

\section{New Business}

\subsection{New CMARA Members}

We verbally voted in the following new CMARA members. Welcome to the club!
\begin{enumerate}
\item Bob Diehl (\texttt{KC1DQT})
\item Mickey Westover (\texttt{WI1Y}) \emph{(Still need application filed)}
\item Maurice Quirke (\texttt{KC1FPI}) \emph{(Still need application filed)}
\item Joe Rich (\texttt{KC1SGT}) \emph{(Still need application filed)}
\end{enumerate}

\subsection{Other New Business}

\begin{enumerate}
\item The ARRL has set up a web page where you can send an email to your members of the US Senate asking them to support the Amateur Radio Parity Act. Visit their website at:\\\texttt{http://www.arrl.org/amateur-radio-parity-act}
\item Don (\texttt{W3DEC}) found an old CMARA binder with lots of historic club information. We want to make sure this information gets properly archived, so Bob (\texttt{KB1VUA}) will be finding some way to archive this information.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}

\begin{enumerate}
\item Dick (\texttt{W1REJ}) upgraded to extra. Congratulations!
\item Marc (\texttt{AB1ZW}) upgraded to extra and got a new call (previously \texttt{KC1DZM}). Congratulations!
\end{enumerate}

\subsection{Other News}

\begin{enumerate}
\item Don (\texttt{W3DEC}) has received shirts from Yaesu that he gave out to various members. The shirts have the \texttt{W3DEC} repeater callsign on them, which Don is proud to announce will be online on Tuesday, September 20\textsuperscript{th}. The repeater will have the same frequency pair as the original \texttt{W1OJ} repeater. Thanks Don!
\item Gill Hayes (\texttt{WK1H}) is looking for people interested in the Assistant ARRL coordinator for the South-East Quadrant. This will cover clubs like CMARA, WPI, WECT, and more. Reach out to Gill for more information. Thanks, Gill!
\item Jim (\texttt{KC1BHD}) has shared with the group that there are two mesh nodes on Skyline Drive for anyone who would like to try out mesh networking. Reach out to Jim for more information. Thanks, Jim!
\end{enumerate}

\section{Next Meeting}

The next meeting will be Thursday, October 20, 2016 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.

\section{Meeting Adjourned}
The meeting was adjourned September 15, 2016 at 8:01 PM PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

Bob (\texttt{KB1VUA}) gave a presentation on Digital Mobile Radio (DMR) and how it's not private. Bob had some recordings of conversations in some large talk-groups which helped understand how the talk-group structure worked. This presentation spawned a great group discussion on how DMR works and how it fits into the hobby. Thanks for the presentation, Bob!

\end{document}
