\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge May 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA May 2016 business meeting was called to order on May 19, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

\texttt{AB2IX},
\texttt{K1BML},
\texttt{K1YYT},
\texttt{KA3RLZ},
\texttt{KB1VUA},
\texttt{KB1YLA},
\texttt{KC1CAR},
\texttt{KC1DTT},
\texttt{KC1FDQ},
\texttt{KM1D},
\texttt{N1EKO},
\texttt{N1KWX},
\texttt{N1TQ},
\texttt{N1ZC},
\texttt{W1BFG},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1IDE},
\texttt{W1IKE},
\texttt{W1PA},
\texttt{W1REJ},
\texttt{W1RJZ},
\texttt{W1TR},
\texttt{W1WER},
\texttt{W3DEC},
\texttt{W4FEB},
\texttt{WA1RCQ},
\texttt{WW2JS}

\subsection{Guests \& Visitors}

\texttt{KC1CAW},
\texttt{N1AZL},
\texttt{N1FF},
\texttt{N1JQ}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}

The secretary's report containing the minutes for the April 2016 meeting was approved as published by verbal vote.

\newpage
\subsection{Treasurer's Report}

The treasurer's report for April 2016 was approved as read by verbal vote.

\subsubsection{Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance (03/31/20156) & \texttt{\$5,197.78} \\
  Income: Membership Dues & \texttt{+\$316.00} \\
  Expense: Bank Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance (03/31/2016) & \texttt{\$5,511.78} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$10,279.56} \\
  \hline
\end{tabular}


\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

No business to report.

\subsubsection{Repeater Trustees Report}

\begin{enumerate}
\item There were no repeater trustees present to provide an update.
\item Members asked about the status of the replacement antenna. It is our understanding that the repeater trustees have been tasked with looking into it, but it doesn't seem like there has been much progress. We will discuss the issue in the board member meeting later this evening.
\end{enumerate}

\subsubsection{Field Day Committee Report}

We are actively preparing for the ARRL 2016 field day. Gerry has been working on getting all the logistics in order. We will spend the majority of this meeting discussing field day, so there is not much to report formally.

\section{Old Business}

There was no old business tabled.

\section{New Business}

\subsection{New CMARA Members}

There were no new CMARA members voted in this month.

\subsection{Other New Business}

There was no other new business to report.

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}

\begin{enumerate}
\item Craig (\texttt{W1CAB}) has upgraded to extra class. Congratulations Craig!
\end{enumerate}

\subsection{Other News}

\begin{enumerate}
\item Mike (\texttt{W1BNC}) is back at home after receiving his cancer treatment. We have no doubt that he'd really appreciate any thoughts your send his way. The treatment likely will restore his good health and we hope that within a couple months he'll be back on the air.
\item If this is your first field day, you'll want to remember to bring everything you need (like a tent or RV, a sturdy table, extension cords, power strips, a generator, ground rods, bug spray, a cell phone charger, snacks, etc).
\item Adrian (\texttt{AB2IX}) will be monitoring the \texttt{W1BIM} repeater and the simplex (\texttt{146.565 Mhz}) during the event from the dining area. He will have a charging station for phones and HT's available for the weekend.
\end{enumerate}

\section{Next Meeting}

The next meeting will be Thursday, June 16, 2016 at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
This will be the last meeting before field day, so we'll be spending time prototyping the network we're going to use and verify N1MM setups. If you're going to bring your computer to field day this year, be sure to bring it to this meeting so we can help you set it up ahead of time.

\section{Meeting Adjourned}
The meeting was adjourned May 19, 2016 at 7:27 PM PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

Bob (\texttt{KB1VUA}) gave a presentation on the field day location. We then opened the floor to discussions pertaining to field day.

\end{document}
