\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge November 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA November 2016 business meeting was called to order on November 17, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:03 PM.

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

\texttt{AB1YH}, \texttt{K1ALN}, \texttt{K1BML}, \texttt{K1RAU}, \texttt{K1YYT}, \texttt{KA1AQP}, \texttt{KB1EZF}, \texttt{KB1VXY}, \texttt{KC1EKJ}, \texttt{KC1ETB}, \texttt{KC1GBK}, \texttt{KC1GIB}, \texttt{KM1D}, \texttt{N1EKO}, \texttt{N1FSK}, \texttt{N1HTB}, \texttt{N1KWX}, \texttt{N1ZC}, \texttt{W1AHM}, \texttt{W1BFG}, \texttt{W1CAB}, \texttt{W1IDE}, \texttt{W1PA}, \texttt{W1REJ}, \texttt{W1RJZ}, \texttt{W1TR}, \texttt{W1WER}, \texttt{W3DEC}, \texttt{W4FEB}, \texttt{WA1JXR}, \texttt{WA1MDD}, \texttt{WA1RCQ}, \texttt{WI1Y}, \texttt{WK1H}, \texttt{WW2JS}

\subsection{Guests \& Visitors}

\texttt{AB1MT}, \texttt{AB1ZW}, \texttt{KB1VXH}, \texttt{KC1SGT}, \texttt{NE1R}, \texttt{W1GJM}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}
The secretary's report for October 2016 was voted in, as published, by verbal vote.

\newpage
\subsection{Treasurer's Report}
The treasurer's report for October 2016 was voted in, as read, by verbal vote.

\subsubsection{October 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$4,605.29} \\
  Income: Membership Dues & \texttt{+\$310.00} \\
  Income: Badges (Extra) & \texttt{+\$5.00} \\
  Expense: Liability Insurance & \texttt{-\$200.00} \\
  Expense: Membership Badges & \texttt{-\$40.19} \\
  Expense: Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance & \texttt{\$4,678.10} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,445.88} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
Membership is growing, which is good. There is nothing else to report.

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
\item There is no new business to report.
\item There has been one report of a potential issue, but we haven't ruled out a local source.
\end{enumerate}

\subsubsection{Field Day Committee Report}
Nothing to report.

\section{Old Business}
There was no old business tabled.

\section{New Business}

\subsection{New CMARA Members}

We verbally voted in the following new CMARA members. Welcome to the club!
\begin{enumerate}
\item George Szarka, Jr. (\texttt{AB1MT})
\end{enumerate}

\subsection{Other New Business}

\begin{enumerate}
\item Bob (\texttt{KB1VUA}) asked for any licensed electricians who would like to volunteer to help fix up our meeting location. We have noticed the church has some non-grounded outlets similar issues. Because of all the Oakdale United Methodist Church has done for us, we'd love to give back.
\item Nominations were held during the November meeting and the following people were nominated for office:
\begin{enumerate}
\item Bob (\texttt{KB1VUA}) has been nominated for the office of president.
\item Brian (\texttt{K1BML}) has been nominated for the office of vice president.
\item Mark (\texttt{W1IDE}) has been nominated for the office of secretary.
\item There are no nominations for the office of treasurer.
\item Lynn (\texttt{WB1CCL}) has been nominated for the office of webmaster.
\item Greg (\texttt{WA1JXR}) has been nominated for a seat in the board of directors.
\item Terry (\texttt{W1TR}) has been nominated for a seat in the board of directors.
\item John (\texttt{WW2JS}) has been nominated for a seat in the board of directors.
\item George (\texttt{AB1MT}) has been nominated for a seat in the board of directors.
\item Jim (\texttt{KC1BHD}) has been nominated for a seat in the board of directors.
\end{enumerate}
\item Next month we will be holding elections for the various positions in the club.

\item Next month we'll be holding our annual potluck. If you would like to sign up for a dish, please reach out to Mark (\texttt{W1IDE}) via email at \texttt{mark@cranstonide.com}. You can see the signup sheets via Google docs at this link: \texttt{http://bit.ly/cmara-potluck-2016}.

\item Greg (\texttt{WA1JXR}) took a moment to remind everyone of Sandy's (\texttt{N1FSK}) work on documenting the club history. \texttt{http://cmara.org/about/history/}

\item John (\texttt{WW2JS}) has shared with the club that he intends on buying merchandise with the club logo. For folks that donate, there are some limited edition mugs that he will be giving out. Reach out to him if you are interested.

\item Mark (\texttt{W1IDE}) asked the club if anyone would be interested in participating in a `holiday club event' where kids could have an opportunity to get on the air and maybe even speak with Santa Claus. There was a good discussion with ideas and concerns. There are special event stations that do exactly this, like \texttt{OF9X}. There are concerns regarding retransmissions over the repeater, so maybe we can just use the repeater locally. Bob (\texttt{KB1VUA}) appointed Mark (\texttt{W1IDE}) as the lead of a spot committee with the purpose of running this project. The committee will report back next month with ideas.
\end{enumerate}

\section{For the Good of the Club}
\begin{enumerate}
\item Don (\texttt{W3DEC}) will be retiring on December 17 and moving to PA before the end of the year. Don wanted to take a moment to thank everyone in the club for all the friendship and good times. Don, on behalf of everyone at CMARA, we all wish you the best on the next leg of your journey.
\item Greg (\texttt{WA1JXR}) won a `Your first HF radio' book at a raffle and gave it to our newest member, George (\texttt{AB1MT}).
\end{enumerate}

\subsection{New Hams \& Upgrades}
There were no new hams nor people with upgrades present.

\subsection{Other News}
No other news.

\section{Next Meeting}
The next meeting will be Thursday, December 15, 2016 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.

\section{Meeting Adjourned}
The meeting was adjourned November 17, 2016 at 7:49 PM PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
Mike (\texttt{N1FF}) gave a great presentation on digital mode operation with a great demo; it was awesome to see how to set these systems up, from start to finish. Thanks, Mike!

\end{document}
