\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge October 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA October 2016 business meeting was called to order on October 20, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:02 PM.

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AB1YH}, \texttt{AB2IX}, \texttt{K1BML}, \texttt{K1HIS}, \texttt{K1RAU}, \texttt{KA3RLZ}, \texttt{KB1EZF}, \texttt{KB1VXY}, \texttt{KC1ACX}, \texttt{KC1DYA}, \texttt{KC1ETB}, \texttt{KC1FDQ},  \texttt{KM1D}, \texttt{N1KWX}, \texttt{W1AHM}, \texttt{W1BFG}, \texttt{W1BNC}, \texttt{W1CAB}, \texttt{W1GD}, \texttt{W1IKE}, \texttt{W1WER}, \texttt{W3DEC}, \texttt{WA1JXR}, \texttt{WA1MDD}, \texttt{WI1Y}, \texttt{WK1H}

\subsection{Guests \& Visitors}

\texttt{AB1ZW}, \texttt{KC1GBK}, \texttt{KC1GIR}, \texttt{KC1GJW}, \texttt{W1GJM}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}

\begin{enumerate}
\item The secretary's report for June 2016 was voted in, as published, by verbal vote.
\item The secretary's report for September 2016 was voted in, as published, by verbal vote.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}

\begin{enumerate}
\item The treasurer's report for May 2016 was voted in, as read, by verbal vote.
\item The treasurer's report for June 2016 was voted in, as read, by verbal vote.
\item The treasurer's report for July 2016 was voted in, as read, by verbal vote.
\item The treasurer's report for August 2016 was voted in, as read, by verbal vote.
\item The treasurer's report for September 2016 was voted in, as read, by verbal vote.
\end{enumerate}

\subsubsection{May 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,511.78} \\
  Income: Membership Dues & \texttt{+\$97.00} \\
  Income: Refund Statement Fee & \texttt{+\$4.00} \\
  Expense: PO Box Rental & \texttt{-\$134.00} \\
  Expense: Membership Badge Mailing & \texttt{-\$7.35} \\
  Expense: Meeting Location Donation & \texttt{-\$300.00} \\
  Expense: Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance & \texttt{\$5,169.43} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,937.21} \\
  \hline
\end{tabular}

\subsubsection{June 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,169.43} \\
  Income: Membership Dues & \texttt{+\$30.00} \\
  Expense: Membership Badges & \texttt{-\$13.63} \\
  Expense: USPS Stamps & \texttt{-\$0.94} \\
  Expense: Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance & \texttt{\$5,182.86} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,950.64} \\
  \hline
\end{tabular}

\subsubsection{July 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,182.86} \\
  Income: Membership Dues & \texttt{+\$50.00} \\
  Expense: Field Day Food & \texttt{-\$462.94} \\
  Expense: Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance & \texttt{\$4,767.92} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,535.70} \\
  \hline
\end{tabular}

\subsubsection{August 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$4,767.92} \\
  Income: Membership Dues & \texttt{+\$27.00} \\
  Expense: Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance & \texttt{\$4,792.92} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,560.70} \\
  \hline
\end{tabular}

\subsubsection{September 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$4,792.92} \\
  Expense: Field Day (Misc) & \texttt{-\$185.63} \\
  Expense: Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance & \texttt{\$4,605.29} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,373.07} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

Nothing to report.

\subsubsection{Repeater Trustees Report}

\begin{enumerate}
\item There is no new business to report.
\item There is nothing to report on the replacement of the \texttt{W1BIM} repeater's transmit antenna. To remind members, there has been a discussion about potentially poor reception of the repeater to the north. It may not be an issue specifically about the antenna, but more about the placement on one of the tower legs.
\end{enumerate}

\subsubsection{Field Day Committee Report}

Nothing to report.

\section{Old Business}

The secretary's report for June 2016 was voted in, during the Secretary's report earlier in the evening.

\section{New Business}

\subsection{New CMARA Members}

We verbally voted in the following new CMARA members. Welcome to the club!
\begin{enumerate}
\item Dwight Ernest (\texttt{KA2CNN})
\item Jamie Giampietro (\texttt{KC1GBK})
\item William Ross (\texttt{N1AZL})
\item Ronald Jabara (\texttt{N1VR})
\item Larry Sieminski (\texttt{KC1FXQ})

\end{enumerate}

\subsection{Other New Business}

\begin{enumerate}
\item Next month's meeting (November) the club will be taking nominations for officers. If you are interested in running for a role, come to the meeting!
\item The club may start to look into its 501(c)(3), but there is a lot to discuss. The club could save some money in taxes and provide donors with tax-exempt donation receipts. There is also a discussion that we could become an education organization.
\item There are a lot of people who haven't paid their 2016 dues. We genuinely believe the lack of payment has been by mistake, so please remember your dues as soon as possible.
\item Gil Hayes (\texttt{WK1H}) was looking for people interested in the assistant section manager. He is proud to announce Greg (\texttt{WA1JXR}) is the new assistant section manager. Thanks Greg!
\end{enumerate}

\section{For the Good of the Club}

\begin{enumerate}
\item Don (\texttt{W3DEC}) shared with the club that his repeater (\texttt{W3DEC}) now has better coverage. The frequency (output) of the repeater is \texttt{448.625 MHz}. The repeater has a standard offset, making the input \texttt{443.625 MHz}, and you'll need a PL (CTCSS) tone of \texttt{88.5 Hz}.
\item The Worcester Country Simplex Net (Held every Tuesday on \texttt{146.565 MHz}) is run by John (\texttt{WW2JS}). Next month, the net will be voting on superlatives of local hams. Things like ``Most Helpful'' will be among the categories. Be sure to check in and share your vote!
\item CMARA used to support Explorer Post years ago. We should start to become more active in the community.
\item Many radio clubs have presenters, and many radio clubs give some nice shwag (like cups or hats). CMARA has not been one of those clubs, but thanks to efforts by John (\texttt{WW2JS}), we may soon have nice things to give away. John has been working on getting some club merchandise and he will be discussing this with the club soon.
\item A question was raised if we have a club banner. Bob \texttt{KB1VUA} has been authorized (during a previous board meeting) to get a new banner. Our old one is ``historic'' to say the least.
\end{enumerate}

\subsection{New Hams \& Upgrades}

There were no new hams nor people with upgrades present.


\subsection{Other News}

No other news.

\section{Next Meeting}

The next meeting will be Thursday, November 17, 2016 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.

\section{Meeting Adjourned}
The meeting was adjourned October 20, 2016 at 7:57 PM PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

Adrian (\texttt{AB2IX}) gave a great presentation on how non-technical hams can start using testing equipment at low cost. He shared equipment lists, testing ideas and explanations of how the components work together. Thanks, Adrian!

\end{document}
