\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge March 2016 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2016 Board of Directors meeting was called to order on March 17, 2016 at 9:13 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes  \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes  \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes  \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes  \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No   \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

None

\subsection{Guests \& Visitors}

None

\section{Primary Discussion}

\subsection{Field Day Location}

\subsubsection{David Proudy High School}

\begin{itemize}
\item If we can find proof of our non-profit status \emph{(501c3)}, we can get a three-day insurance policy for \$175. This insurance policy is needed for use of the hill at David Proudy High School.
\item Bathroom costs are about \$20-\$30 per hour. If we had valid non-profit status, this may be waived. Since we may not be able to afford the asked cost, we could rent a porta-potty for cheaper.
\end{itemize}

\subsubsection{Moose Hill}

\begin{itemize}
\item Additional \$400 - \$500 for use of the location, still would need a porta-potty.
\end{itemize}

\subsubsection{Mercy Centere}

\begin{itemize}
\item We'd run as 5A/6A/7A. If we run generators outside, we still could operate as Alpha class. Only the radio would need to be on the generators. Computers, lights, etc could be commercially powered.
\item Out of the weather
\item The building is 24 feet tall.
\item There is a cell tower present at the location, but Bob (\texttt{KB1VUA}) does not get any interference from it.
\item There are no high tension wires there.
\item We can still make use of the motor home.
\end{itemize}

\subsection{Non-Profit Status}
\begin{itemize}
\item We need to consider hiring lawyer with corporate experience to straighten out our 501c filings and the corporation documents.
\item We currently have multiple EIN numbers that show up in the search.
\item Mark (\texttt{W1IDE}) will search for paralegal, and will email the board members with findings.
\end{itemize}

\subsection{Club Document Backups}
\begin{itemize}
\item We need to have backups of important club documents. The keys to the kingdom should not be in the hands of one ham.
\item John (\texttt{WW2JS}) has offered us to store copies of documents in his safe. Mark (\texttt{W1IDE}) also offered his safe and use of his server (which has redundant backups).
\end{itemize}


\subsection{Interest Survey}
Dick (\texttt{W1REJ}) will send out a survey to find out what people want out of the club (presentations, activities, etc).

\subsection{Equipment Offerings}
Tom (\texttt{NE1R}) gave Bob (\texttt{KB1VUA}) some military equipment. Bob will offer it to club members first before bringing it to nearfest. He plans on bringing it to the next meeting.

\subsection{ARRL Materials}

Terry (\texttt{W1TR}) is still actively working on getting ARRL materials.

\section{Meeting Adjourned}
The meeting was adjourned March 17, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 9:39 pm.

\end{document}
