\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge March 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2016 business meeting was called to order on March 17, 2016 at 7:13 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes  \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes  \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes  \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes  \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No   \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{K1BML},
\texttt{K1YYT},
\texttt{KA1AQP},
\texttt{KB1VUA},
\texttt{KB1VXY},
\texttt{KC1AWS},
\texttt{KC1DZM},
\texttt{KM1D},
\texttt{N1EKO},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1IDE},
\texttt{W1IKE},
\texttt{W1REJ},
\texttt{W1TR},
\texttt{W3DEC},
\texttt{W4FEB},
\texttt{WA1IKM},
\texttt{WA1JXR},
\texttt{WA1MDD},
\texttt{WA1RCQ},
\texttt{WK1H}


\subsection{Guests \& Visitors}
\texttt{AB1YH},
\texttt{AB2IX},
\texttt{N1HTB},
\texttt{K1ALN},
\texttt{K1GNR},
\texttt{KA3RLZ},
\texttt{KB1VXH},
\texttt{KC1BHD},
\texttt{KC1CAR},
\texttt{N1FF},
\texttt{N1KWX},
\texttt{N1TQ},
\texttt{N1ZC},
\texttt{NE1R},
\texttt{W1BFG},
\texttt{W1PA},
\texttt{WW2JS}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}

The secretary's report containing the minutes for the January 2016 and February 2016 meetings were  approved as published by verbal vote.

\newpage
\subsection{Treasurer's Report}

The treasurer's reports for the January 2016 and February 2016 minutes were approved as read by verbal vote.

\subsubsection{January 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance (12/31/2015) & \texttt{\$4,214.05} \\
  Income: Membership Dues & \texttt{+\$685.00} \\
  Expense: Bank Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance (01/31/2016) & \texttt{\$4,897.05} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,664.84} \\
  \hline
\end{tabular}

\subsubsection{February 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance (01/31/2016) & \texttt{\$4,897.05} \\
  Income: Membership Dues & \texttt{+\$315.00} \\
  Expense: Bank Paper Statement Fee & \texttt{-\$2.00} \\
  Expense: Membership Badges & \texttt{-\$80.27} \\
  Ending Checking Balance (02/29/2016) & \texttt{\$5,129.78} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,897.56} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
Dick (\texttt{W1REJ}) spoke with a gentleman by the name of Tony regarding information on obtaining a license.

\subsubsection{Repeater Trustees Report}

Nothing to report.

\subsubsection{Field Day Committee Report}

\begin{enumerate}
\item Due to legality issues, Rutland may not be an ideal location for field day this year. The committee still needs to look into insurance policies for that weekend and obtaining 501C status.
\item We are currently in discussions regarding the field day location this year. Some of the options are:
\begin{enumerate}
\item Mercy Centre School (Worcester) - We're currently treating this as a last resort. They would charge us around \$20 per hour for the use of the building.
\item Moose Hill (Spencer) - The club has been using this location for some time, but the land is under new management and the cost may have increased.
\end{enumerate}
\end{enumerate}

\section{Old Business}

There was no old business tabled.

\section{New Business}

\begin{enumerate}
\item Leo Bolduc (\emph{no license}) became a CMARA member by verbal vote.
\end{enumerate}



\section{For the Good of the Club}

\begin{enumerate}
\item Bob Beausoleil (\texttt{KA1OTQ}) became a silent key on March 12, 2016.  He was instrumental in events such as the Sutton chain of lights, he conducted the Sunday morning RACES net and he was a past president of CMARA. Please keep him and his family in your thoughts.
\item Herb (\texttt{KC1CAR}) donated a RFID blocking wallet to the club. John (\texttt{WW2JS}) won the wallet from a random drawing.
\end{enumerate}

\section{Next Meeting}

The next meeting will be Thursday, April 21, 2016 at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The presentation will be by Mark Richards (\texttt{K1MGY}), ``Introduction to Skywarn''. Mark is the PART (Westford) Skywarn Coordinator. He collects data from amateur radio operators participating in Skywarn nets, passing the data on to NWS Taunton.

\section{Meeting Adjourned}
The meeting was adjourned March 17, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:41 pm.

\section{Post-Meeting Presentation}
We had two presentations this month.
\begin{enumerate}
\item Gerry (\texttt{W1GD}) gave a fantastic presentation on the story of the 160 meter contesting team. Awesome details on real-world problem solving and how the team was so successful. Thanks Gerry!
\item Jim (\texttt{KC1BHD}) gave a quick presntation on mesh networking. This presentation is a runthrough of the presentation Jim will give to WECT (The Worcester Emergency Communications Team) to propose setting up a central MA mesh network. Awesome details, thanks Jim!
\end{enumerate}

\end{document}
