\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge April 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA April 2016 business meeting was called to order on April 21, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

\texttt{AB2IX},
\texttt{K1BML},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA3RLZ},
\texttt{KB1VUA},
\texttt{KC1DTT},
\texttt{KC1ETB},
\texttt{KC1FDQ},
\texttt{KM1D},
\texttt{N1EKO},
\texttt{N1FSK},
\texttt{N1HTB},
\texttt{N1KWX},
\texttt{N1ZC},
\texttt{NG1I},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1GJM},
\texttt{W1IDE},
\texttt{W1IKE},
\texttt{W1REJ},
\texttt{W1RJZ},
\texttt{W1TR},
\texttt{W1WER},
\texttt{W4FEB},
\texttt{WA1MDD},
\texttt{WA1RCQ},
\texttt{WK1H},
\texttt{WW2JS}

\subsection{Guests \& Visitors}

\texttt{K1GNR},
\texttt{KC1AOG},
\texttt{N1EOP},
\texttt{N1FF},
\texttt{NE1R},
\texttt{W1BFG}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}

The secretary's report containing the minutes for the March 2016 meeting was approved as published by verbal vote.

\newpage
\subsection{Treasurer's Report}

The treasurer's report for March 2016 was approved as read by verbal vote.

\subsubsection{March 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance (02/28/20156) & \texttt{\$5,129.78} \\
  Income: Membership Dues & \texttt{+\$70.00} \\
  Expense: Bank Paper Statement Fee & \texttt{-\$2.00} \\
  Ending Checking Balance (03/31/2016) & \texttt{\$5,197.78} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,965.56} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

\begin{enumerate}
\item Terry (\texttt{W1TR}) is going to follow up with the league (ARRL) because it seems like the request for some materials has been lost.
\item There was a question of the success of the mailings we've been doing. Apparently, we've only gained a few members (4-5) specifically from the mailing, so we may not do that again. Most people hear about the club through the repeater.
\item We should add a checkbox or field on the application form to tell us where you heard about the club. This would give us very helpful feedback.
\end{enumerate}

\subsubsection{Repeater Trustees Report}

There were no repeater trustees present.

\subsubsection{Field Day Committee Report}

\begin{enumerate}
\item We have a 2016 field day site, the Aldrich Astronomical Society's private field in Oakham, MA.
\item The location is 3-4 acres in size and surrounded by trees.
\item The land is private, but we have permission to be there.
\item Weather dependent, the astronomical club may bring out their telescopes and/or open the observatory.
\item Because we are guests of the Aldrich Astronomical Society, we can't open the CMARA field day station to the public this year. Family and friends are fine. There is a concern about the GOTA (Get-On-The-Air) station, but there isn't much we can do.
\end{enumerate}

\section{Old Business}

There was no old business tabled.

\section{New Business}

\begin{enumerate}
\item If you are not receiving the monthly emails which include the meeting minutes, please reach out the club secretary, Mark (\texttt{W1IDE}). The mailing list has transfered many hands, but it's now in a stable system so we should be able to get everyone.
\end{enumerate}

\section{For the Good of the Club}

\begin{enumerate}
\item Olof Johnson (\texttt{W1OCJ}) became a silent key on March 30, 2016. Many of us shared QSOs with Olof in the months leading to his passing. Please keep him and his family in your thoughts.
\item Charles Lord (\texttt{N1WAS}) became a silent key on April 11, 2016. We remember Charles as a George's Old Timer's Net control and an active member of the amateur radio community. Please keep him and his family in your thoughts.
\end{enumerate}

\section{Next Meeting}

The next meeting will be Thursday, May 19, 2016 at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
We will be discussing logistics regarding field day and what actions are still required. If you're interested in what field day has to offer, or if are able to help that day, please come and share. If you plan on bringing your computer to field day, please bring it May 19 with \texttt{N1MM} installed. \texttt{N1MM} can be downloaded from \texttt{http://n1mm.hamdocs.com/}.

\section{Meeting Adjourned}
The meeting was adjourned April 21, 2016 at 7:50 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

The presentation this month was ``Introduction to SKYWARN'' by Mark Richards (\texttt{K1MGY}). Mark is the PART (Westford) SKYWARN Coordinator. He collects data from amateur radio operators participating in SKYWARN nets, passing the data on to NWS Taunton.

\end{document}
