% Notes provided by Brian, K1BML

\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge June 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA June 2016 business meeting was called to order on June 16, 2016 at 7:15 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & No  \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & No \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members \& Guests Present}

\texttt{K1ALH}, \texttt{K1BML}, \texttt{K1RAU}, \texttt{KB1VUA}, \texttt{KB1VXH}, \texttt{KB1VXY}, \texttt{KB1YLA}, \texttt{KC1FDQ}, \texttt{KM1D}, \texttt{N1AZL}, \texttt{N1EKO}, \texttt{N1FF}, \texttt{N1KWX}, \texttt{N1TQ}, \texttt{N1ZC}, \texttt{NG1I}, \texttt{W1AHM}, \texttt{W1GD}, \texttt{W1PA}, \texttt{W1REJ}, \texttt{W1RJZ}, \texttt{W1WER}, \texttt{W3DEC}, \texttt{W4FEB}, \texttt{WA1BZQ}, \texttt{WA1IKM}, \texttt{WA1MDD}, \texttt{WA1RCQ}, \texttt{WW2JS}

\section{Reports}

\subsection{Secretary's Report}

The Secretary, Mark (\texttt{W1IDE}), was absent. Voting tabled until next month.

\newpage
\subsection{Treasurer's Report}

The treasurer's report for May 2016 was approved as read by verbal vote.

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

No business to report.

\subsubsection{Repeater Trustees Report}

Nothing to report.

\subsubsection{Field Day Committee Report}

Nothing to report.

\section{Old Business}

There was no old business tabled.

\section{New Business}

\subsection{New CMARA Members}

\begin{enumerate}
\item William Ross (\texttt{N1AZL}) became a member of CMARA by verbal vote. Welcome to the club!
\end{enumerate}

\subsection{Other New Business}

There was no other new business to report.

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}

There were no new hams nor upgrades this month.

\subsection{Other News}

There was no other news.

\section{Next Meeting}

The next meeting will be Thursday, September 15, 2016 at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\section{Meeting Adjourned}
The meeting was adjourned June 16, 2016 at 7:35 PM PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

No notes recorded on the post-meeting presentation.

\end{document}
