\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/cmara/meeting-minutes}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge May 2016 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA May 2016 Board of Directors meeting was called to order on May 19, 2016 at 9:08 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes  \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

None

\subsection{Guests \& Visitors}

None

\section{Primary Discussion}

\subsection{\texttt{W1BIM} Antenna}
\begin{enumerate}
\item We need to determine the status of the \texttt{W1BIB} repeater's antenna with the repeater committee. We want to make sure the CMARA and the \texttt{W1BIM} repeater does not get a bad name for interfering with other signals. The current antenna has a poor transmission pattern to the Northeast, and it may be strongest to the Southwest (away from the majority of it's users).

\item Because of the club by-laws, we can not make the repeater committee take action. We can only urge them to investigate. Bob will follow up with the repeater committee to see what their thoughts are.

\item There is also a question if the existing radio tower is condemned. If so, this may prevent us from replacing the antenna until a new tower is erected.
\end{enumerate}
\subsection{501(c)(7) Non-Profit Club Status}
\begin{enumerate}
\item The bank has our Tax ID on file.
\item The list of officers needs to be updated with the state. Mark (\texttt{W1IDE}) will work with Jim (\texttt{N1EKO}) to file the update.
\end{enumerate}

\subsection{Field Day}
\begin{enumerate}
\item Bob (\texttt{KB1VUA}) has been granted permission to spend up to \$300.00 for a porta-potty for field day by verbal vote.
\item Art (\texttt{WA1RCQ}) has been granted permission to spend up to \$600.00 for food for field day by verbal vote.
\item Mark will send out a survey that will ask members about field day. The survey will seek details like how many people are coming, eating, bringing guests, etc. Mark will share the results by the next meeting.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned May 19, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 9:44 pm.

\end{document}
