\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge February 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA February 2016 business meeting was called to order on February 18, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes              \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes              \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No               \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No               \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No               \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes              \\
  Harold Carlson    & \texttt{N1ZC}     & Yes              \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes              \\
  Terry Glagowski   & \texttt{W1TR}     & Yes              \\
  Randy Dore        & \texttt{W4FEB}    & Yes              \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes              \\
  \hline
\end{tabular}

\subsection{Members Present}

\texttt{K1BML},
\texttt{K1RAU},
\texttt{KA1AQP},
\texttt{KB1VXY},
\texttt{KC1ETB},
\texttt{N1FSK},
\texttt{W1BFG},
\texttt{W1CAB},
\texttt{W1IKE},
\texttt{W3DEC},
\texttt{WA1JXR}

\subsection{Guests \& Visitors}

\texttt{KA3RLZ},
\texttt{KB1CIF},
\texttt{N1HTB},
\texttt{NE1R},
\texttt{W1PA}

\noindent\\
\emph{(Note: If we haven't received your dues, you're considered a guest. If you feel this is a mistake, contact the club treasurer.)}

\section{Reports}

\subsection{Secretary's Report}

The secretary's report for containing the minutes for the January 2016 business meeting were not read nor approved. They will be read and a vote will be taken during the March meeting.

\newpage
\subsection{Treasurer's Report}

The treasurer's report for containing the minutes for the January 2016 business meeting were not read nor approved. They will be read and a vote will be taken during the March meeting.

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

Nothing to report.

\subsubsection{Repeater Trustees Report}

Nothing to report.

\subsubsection{Field Day Committee Report}

Nothing to report.

\section{Old Business}

There was no old business tabled.

\section{New Business}

\begin{enumerate}
\item We had one new membership application. Ray (\texttt{KC1EZX}) became a CMARA member by verbal vote.
\item Mark, (\texttt{K1MGY}) has offered to present to the club about the Skywarn program. He also expressed interest in offering a class on the subject to train potential Skywarn observers.

\end{enumerate}

\section{For the Good of the Club}

Nothing to report.

\section{Next Meeting}

The next meeting will be Thursday, March 17, 2016 at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The presentation has not yet been determined.

\section{Meeting Adjourned}
The meeting was adjourned February 18, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

After the adjournment of the business meeting, Don (\texttt{W3DEC}), gave his presentation on Near Vertical Incidence Skywave (NVIS). It's used for local communications, usually 0-250 statute miles. There are various websites (See Don at the next meeting if you missed them) that can provide critical frequency predictions for each band at different times of the day.

\end{document}
