\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/cmara/meeting-minutes}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge April 2016 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA April 2016 Board of Directors meeting was called to order on April 21, 2016 at 9:00 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes  \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes  \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes  \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes  \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No   \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

None

\subsection{Guests \& Visitors}

None

\section{Primary Discussion}

\subsection{Field Day}
\begin{enumerate}
  \item Gerry (\texttt{W1GD}) went and paced off the field.
  \item We will want to turn down public announcements; since we are guests of Bob's astronomy club.
  \item What are the points we're losing out on? Public space / Info booth?
  \item The field has a swamp to the west, so propagation should be good.
  \item The grass is mowed short, so we do not need to worry about ticks.
  \item It's possible that people will file noise complaints. To avoid this, we can point our generators away from houses and put a vehicle or shield around them.
  \item The field is about 300 by 400 feet, so it is bigger than Moose Hill.
  \item Who will be our safety officer? Will it be Brian (\texttt{K1BML})?
\end{enumerate}

\subsection{501c Status}

No progress has been made on clearing up our 501c status.

\subsection{Next Presentation}

We'll be discussing field day.

\section{Meeting Adjourned}
The meeting was adjourned April 21, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 9:39 pm.

\end{document}
