\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{Page \thepage\ of \pageref{LastPage}}
\rfoot{}

\begin{document}

\begin{center}
{\huge November 2016 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA November 2016 Board of Directors meeting was called to order on November 17, 2016 at 9:30 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes  \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes  \\
  Dick Jubinville   & \texttt{W1REJ}    & No \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

None

\subsection{Guests \& Visitors}

None

\section{Primary Discussion}

\subsection{Presentations}

The board needed to devise a list of potential presentations for the January meeting. The presentation will be decided in December.

\begin{enumerate}
  \item Terry (\texttt{W1TR}) on YCCC (Yankee Clipper Contest Club)
  \item Terry (\texttt{W1TR}) on Antenna control
  \item Sandy (\texttt{N1FSK}) on CMARA history
  \item Gerry (\texttt{W1GD}) on field day results
  \item Scott (\texttt{KB1EZF}) on RS232 serial communications
  \item Bill (\texttt{W1PA}) on satellite operation
  \item Tom (\texttt{NE1R}) on knot tying
  \item Adrian (\texttt{AB2IX}) on Non Technologist Ham Test Bench - 2nd in series (planned for March or April 2017)
  \item Video as a backup for lack of presentation
\end{enumerate}

\subsection{Flea Market}
Bob (\texttt{KB1VUA}) would like to see the club host a flea market in the next year. It will give the club some viability, plus potentially raise some money. We haven't yet sought approval since at this point it's just an idea.

\noindent
\\It was also mentioned that we could have a ``white elephant'' table at the meetings, where members could tag and share items they'd like to sell. Ideally, the club would get some portion of the profit, but nothing was decided.

\subsection{Treasurer's Request}

Jim (\texttt{N1EKO}) has requested that he combine the funds from the radio sales (\$1,268.04) into the general club checking account. The request was approved by verbal vote from the board.

\subsection{Merchandise}
John (\texttt{WW2JS}) is actively working on developing new merchandise opportunities. He's recently picked up a card printer that allows him to print ID cards. There is more to come on this front.

\section{Next Month's Presentation}
Next month will be the voting of officers and board members, along with the annual potluck.

\section{Meeting Adjourned}
The meeting was adjourned November 17, 2016 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 10:15 PM.

\end{document}
