\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}
% \pagestyle{fancyplain}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{Page \thepage\ of \pageref{LastPage}}
\rfoot{}

\begin{document}

\begin{center}
{\huge January 2016 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA January 2016 business meeting was called to order on January 21, 2016 at 7:07 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}

\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes              \\
  Vice President    & Art Kass       & \texttt{WA1RCQ}   & Yes              \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes              \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes              \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No               \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes              \\
  Harold Carlson    & \texttt{N1ZC}     & No               \\
  Dick Jubinville   & \texttt{W1REJ}    & Yes              \\
  Terry Glagowski   & \texttt{W1TR}     & Yes              \\
  Randy Dore        & \texttt{W4FEB}    & Yes              \\
  Johnathan Sherman & \texttt{WW2JS}    & No               \\
  \hline
\end{tabular}

\subsection{Members Present}

\texttt{AA2S},
\texttt{K1BML},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA1AQP},
\texttt{KB1EZF},
\texttt{KB1LOU},
\texttt{KB1QZD},
\texttt{KB1VUA},
\texttt{KB1VXY},
\texttt{KB1YLA},
\texttt{KC1AOG},
\texttt{KC1AWS},
\texttt{KC1DTT},
\texttt{KM1D},
\texttt{N1EKO},
\texttt{N1FF},
\texttt{N1SFK},
\texttt{NE1R},
\texttt{NG1I},
\texttt{W1AHM},
\texttt{W1BFG},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1IKE},
\texttt{W1PA},
\texttt{W1REH},
\texttt{W1RJZ},
\texttt{W1TR},
\texttt{W1WER},
\texttt{W3DEC},
\texttt{W4FEB},
\texttt{WA1IKM},
\texttt{WA1JXR},
\texttt{WA1MDD},
\texttt{WA1RCQ}

\subsection{Guests \& Visitors}
\texttt{K1ALN},
\texttt{KB1VXH},
\texttt{KC1DYA},
\texttt{KC1ETB},
\texttt{N1AUP},
Becky Ide

\section{Reports}

\subsection{Secretary's Report}

The secretary's report for containing the minutes for the December 2015 meeting were read by CMARA secretary Mark (\texttt{W1IDE}). It was approved as read by a voice vote.

\newpage
\subsection{Treasurer's Report}
Jim (\texttt{N1EKO}), read the November 2015 treasurer's report. It was approved as read by a voice vote. A summary of the report is included below:
\begin{center}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Income: Membership Dues & \texttt{+\$40.00} \\
  \hline
  \hline
  Expense: Member Badges & \texttt{-\$41.00} \\
  Expense: USPS Postage & \texttt{-\$9.80} \\
  \hline
  \hline
  Beginning Balance (10/31/2015) & \texttt{\$4,099.41} \\
  Total Income & \texttt{+\$40.00} \\
  Total Expenses & \texttt{-\$50.80} \\
  Ending Balance (11/30/2015) & \texttt{\$4,088.61} \\
  \hline
  \hline
  CD & \texttt{\$4,738.53} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$8,827.14} \\
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  Radio Donation Sales & \texttt{\$1,830.00} \\
  \hline
\end{tabular}
\end{center}

\noindent
Jim (\texttt{N1EKO}), read the December 2015 treasurer's report. It was approved as read by a voice vote. A summary of the report is included below:

\begin{center}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Income: Membership Dues & \texttt{+\$112.00} \\
  Income: Donations & \texttt{+\$30.00} \\
  \hline
  \hline
  Expense: Member Badges & \texttt{-\$1.56} \\
  Expense: State of MA Non-Profit Filing & \texttt{-\$15.00} \\
  \hline
  \hline
  Beginning Balance (11/30/2015) & \texttt{\$4,088.61} \\
  Total Income & \texttt{+\$142.00} \\
  Total Expenses & \texttt{-\$16.56} \\
  Ending Balance (12/31/2015) & \texttt{\$4,214.05} \\
  \hline
  \hline
  CD & \texttt{\$4,738.53} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$8,952.58} \\
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  Radio Donation Sales & \texttt{\$1,830.00} \\
  \hline
\end{tabular}
\end{center}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

Nothing to report.

\subsubsection{Repeater Trustees Report}

Dan (\texttt{K1RAU}) asked if the \texttt{W1BIM} repeater was set to ID more often over the last week or so. Greg (\texttt{WA1JXR}) informed the club that he increases the frequency of the ID when there is a club announcement on the repeater. We can expect the ID rate to return to normal after the meeting. Other than that, nothing was reported.

\subsubsection{Field Day Committee Report}

Bob (\texttt{KB1VUA}) mentioned that there will be a group formed to help the new field day chairman, Jerry (\texttt{W1GD}).

\section{Old Business}

There was no old business tabled.

\section{New Business}

\begin{enumerate}
\item We had two new membership applications. Craig (\texttt{KC1ETB}) and Kevin (\texttt{KC1DYA}) both became CMARA members by verbal vote.

\item Bob (\texttt{KB1VUA}) brought up that during our December elections, we failed to add Greg (\texttt{WA1JXR}) onto the ballot for Board of Directors. Greg has been on the board for some time now, and because of a communications breakdown between the officers, he was not included in the vote. It was agreed that there will be no action taken and Greg will simply have a year off and will be included in the next ballot.

\item Don (\texttt{W3DEC}) made a motion to purchase new repeater equipment for no more than \$1,500.00. President Bob (\texttt{KB1VUA}) mentioned that topic is normally handled by the board of directors during their meeting and tabled it for the meeting later in the evening.

\item Jerry (\texttt{W1GD}) mentioned that field day will be on June 25 and 26 this year. He wants to make sure we secure the same site (the hill at David Prouty High School) and keep the same level of excitement.

\item  Mark (\texttt{W1IDE}) discussed the need for internal communication improvements within our own club. He will meet with the membership committee to discuss how to keep the members informed, as that is one of the committee's responsibilities.

\item Bob (\texttt{KB1VUA}) announced that one of our board members, Johnathan (\texttt{WW2JS}), was home sick that evening recovering from a virus.

\item Adrian (\texttt{AB2IX}) announced that he'll be giving his talk ``From Spark Gap to Ardunio'' on February 4th at 7:30 PM for the Framingham Amateur Radio Association (FARA). It will be in the first floor training room of the Framingham Police Station (1 William Welch Way, Framingham). All are welcomed to attend.

\item Greg (\texttt{WA1JXR}) gave a quick update on the modulated CW club project. He and Bill (\texttt{AA2S}) are close to having a prototype board ready for their testing.

\item Mark (\texttt{W1IDE}) made a motion to appoint a temporary secretary for the month of February since he will be out of the area. Bob (\texttt{KB1VUA}) said that they'd get another board member to fill the slot for the day.
\end{enumerate}


\section{For the Good of the Club}

\begin{enumerate}

\item There were no new licenses or new upgrades to report this month.

\item Nobody wanted to have an antenna party.

\item The next ham radio flea market is on Feburary 13 at the Marlborough Middle School (25 Union Street, Marlborough, MA 01752). It's sponsored by the Algonquin Amateur Radio Club. To see more hamfests, check out \texttt{www.arrl.org/hamfests/search}.

\item Adrian (\texttt{AB2IX}) informed everyone that Near-Fest will be held the last weekend of April (April 29 and 30) in Deerfield, NH. We can expect tickets to go online mid-Feburary. Remember to get your hotel reservations soon if you need one. For more information on Near-Fest, check out \texttt{www.near-fest.com}.

\end{enumerate}


\section{Next Meeting}

The next meeting will be Thursday, February 18, 2016 at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The presentation will be determined by the board of director's meeting later in the evening.

\section{Meeting Adjourned}
The meeting was adjourned at 7:34 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
