\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge November 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA November 2017 board meeting was called to order on November 16, 2017 at 8:55 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & No  \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & No  \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KA3RLZ},
\texttt{KC1GIB},
\texttt{W1PA}

\subsection{Guests \& Visitors}
Christopher Wentworth

\section{Primary Discussion}

\subsection{December Meeting}
\begin{enumerate}
  \item Bob (\texttt{KB1VUA}) will not be present at the December meeting. Vice President Brian (\texttt{K1BML}) will be taking over for the meeting.
  \item December will be our elections and our annual potluck.
  \item Mark (\texttt{W1IDE}) will send out the food sign-ups as he has in prior years.
  \item Both Adrian (\texttt[AB2IX]) and Mike (\texttt{W1BNC}) will be retiring this month, so the potluck can double as a small celebration for them.
\end{enumerate}

\subsection{January Meeting}
\begin{enumerate}
  \item We will be having the Skype presentation from DXEngineering.
  \item Mark (\texttt{W1IDE}) has offered his laptop to run the Skype session, but we will still need to sort out WiFi and test everything prior to the presentation.
  \item We may have a board meeting prior to the January meeting to help sort things out with the new board members and officers. The first week in January was proposed, but nothing formalized at this point.
\end{enumerate}

\subsection{Additional Responsibilities}
\begin{enumerate}
  \item Bob (\texttt{KB1VUA}) proposed asking for at least two volunteers to fill the slots of new responsibilities. We'd be looking for someone to organize presentations and someone to organize the refreshments.
  \item Should this be specific to the board (is there a requirement that the organizers are board members)? We will propose this to the larger group to see if anyone is interested.
  \item Having a `lead person' on these components will make the board's life easier, they'll be able to drive this with more quality since that will be their focus.
\end{enumerate}

\subsection{Mike's Station Tour}
\begin{enumerate}
  \item There were approximately 16 people who responded to the survey online, but it's not hard to imagine there are more people interested. This gives a good starting point for numbers.
  \item Bob (\texttt{KB1VUA}) will follow up with Mike (\texttt{W1BNC}) and find out when works best for him.
\end{enumerate}

\section{Next Month's Presentation}
Elections and the annual potluck will be held.

\section{Meeting Adjourned}
The meeting was adjourned November 16, 2017 at 8:48 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
