\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge June 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA June 2017 business meeting was called to order on June 15, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:14 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AE1DX},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA1AQP},
\texttt{KA3RLZ},
\texttt{KB1JUG},
\texttt{KB2SAE},
\texttt{KC1DYA},
\texttt{KC1ETB},
\texttt{KC1FPI},
\texttt{KC1GIB},
\texttt{KC1HOZ},
\texttt{KM1D},
\texttt{N1AZL},
\texttt{N1FF},
\texttt{N1FSK},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1DYQ},
\texttt{W1GD},
\texttt{W1JKS},
\texttt{W1PA},
\texttt{W1WER},
\texttt{WA1JXR},
\texttt{WA1MDD},
\texttt{WA1RCQ}

\subsection{Guests \& Visitors}
Christopher Wentworth,
\texttt{K1TIN},
\texttt{KA1ZI},
\texttt{KC1DMM},
\texttt{KC1SGT}

\noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
The May 2017 minutes were summarized by Mark (\texttt{W1IDE}) and approved by the club via voice vote.

\newpage
\subsection{Treasurer's Report}
As Jim (\texttt{N1EKO}) was absent, the treasurers report has been tabled.

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
No one from the membership committee was present, so any reports will be tabled.

\subsubsection{Repeater Trustees Report}
No one from the repeater trustees group was present, so any reports will be tabled.

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item The food still needs planning, there haven't been any volunteers yet and that's a concern.
  \item Morris (\texttt{KC1FPI}) has offered to bring a large cooler for our use.
  \item There was a discussion about using crock-pots, and the use of them at field day. It will keep things hot and ready for a long enough time.
  \item We still have major power concerns. No one has stepped up to lead that effort.
  \item We still need operators. There are plenty of available slots if anyone wants to operate.
  \item In summary, we're doing okay, but we still need more participation.
  \item The address of the site will be posted at the end of the meeting minutes.
\end{enumerate}

\section{Old Business}
\begin{enumerate}
  \item Bob (\texttt{KB1VUA}) did investigate the porta-potty situation. We are good to go on this front.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}

In the absence of Jim (\texttt{N1EKO}), all new membership applications will be tabled.

\subsection{Other New Business}
\begin{enumerate}
  \item Herb (\texttt{KC1GIB}), as the coordinator of George's Old Timer's Net, is looking to fill the Wednesday night operator's slot. If you're interested, please reach out to him.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
There were no hams nor upgrades present at the meeting.

\subsection{Other News}
\begin{enumerate}
  \item Tom (\texttt{NE1R}) informed the club that the Boxboro hamfest will have some good presentations this year. To learn more, visit \texttt{www.boxboro.org}.
  \item Jim (\texttt{N1EKO}) is home with a health issue; if you have some spare time, he'd love the thought.
  \item We say goodbye to Chet Lawrence (\texttt{KC1BCV}) as he has become a silent key. We remember Chet as a member of CMARA and a member of the greater ham community. Please keep him and his family in your thoughts.
  \item We thank Gerry (\texttt{W1GD}) for his presentation last month. It was a great introduction for this year's field day.
  \item Adrian (\texttt{AB2IX}) reminds folks to keep in mind the weather for field day. There may be some rain, so please come prepared.
  \item Brian (\texttt{K1BML}) wanted to remind people about the policy on red flashlights at field day. Because we may be sharing the field with the astronomy club, we need to use only red flashlights and keep headlights off or at least pointed away from the field.
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, September 21, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583. The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item There will be a board meeting after field day. The exact date and location is yet to be determined. All club members are welcome, but not required.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned June 15, 2017 at 7:38 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
\begin{enumerate}
  \item The 2017 CMARA Field Day site is:\\
  \begin{tabular}{|rl|}
    \hline
    \textbf{Name} & Aldrich Astronomical Society, Inc. \\ \hline
    \textbf{Address} & 925 East Hill Road East\\
    &  Oakham, MA. 01068 \\ \hline
    \textbf{Latitude \& Longitude} & 42.332419, -72.012101 \\ \hline
    \textbf{Degrees, Minutes, Seconds} & 42$^{\circ}$ 19' 56.9454'' \\
    & -72$^{\circ}$ 0' 42.5088'' \\ \hline
    \textbf{Contact Person} & Bob (\texttt{KB1VUA}) \\ \hline
  \end{tabular}
  \item Terry (\texttt{W1TR}) gave a good presentation on the use of \texttt{N1MM+}, which we will be using at field day. If you missed the presentation and plan on operating at field day, please review the \texttt{N1MM+} tool.
\end{enumerate}

\end{document}

