\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/cmara/meeting-minutes}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge January 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA January 2017 business meeting was called to order on January 19, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:23 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No  \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}      & \textbf{Callsign} & \textbf{Present} \\ \hline
  Greg Algieri       & \texttt{WA1JXR}   & No  \\
  George Szarka, Jr. & \texttt{AB1MT}    & Yes \\
  James Garner       & \texttt{KC1BHD}   & No  \\
  Terry Glagowski    & \texttt{W1TR}     & Yes \\
  Johnathan Sherman  & \texttt{WW2JS}    & Yes \\
  Randolph Dore      & \texttt{W4FEB}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AB1MT},
\texttt{AB2IX},
\texttt{K1BML},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA1AQP},
\texttt{KA3RLZ},
\texttt{KB1VUA},
\texttt{KB1VXY},
\texttt{KC1ACX},
\texttt{KC1DYA},
\texttt{KC1FPI},
\texttt{KC1GIB},
\texttt{KM1D},
\texttt{N1EKO},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1PA},
\texttt{W1REJ},
\texttt{W1RJZ},
\texttt{W1TR},
\texttt{W1WER},
\texttt{W4FEB},
\texttt{WA1RCQ},
\texttt{WI1Y},
\texttt{WW2JS}

\subsection{Guests \& Visitors}

\texttt{AE1DX},
\texttt{KC1FDQ},
\texttt{KC1SGT},
\texttt{W1ABP}*,
\texttt{W3SJP}*\\

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
The secretary was absent due to a family emergency. No meeting minutes were voted on. This will be tabled until February.

\newpage
\subsection{Treasurer's Report}
The treasurer's report was voted in by verbal vote.

\subsubsection{December 2016 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$4,821.54} \\
  Income: Membership Dues & \texttt{+\$42.00} \\
  Expense: Membership Badges & \texttt{-\$18.94} \\
  Expense: Photocopies & \texttt{-\$8.77} \\
  Ending Checking Balance & \texttt{\$4,835.83} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$9,603.61} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
Nothing to report.

\subsubsection{Repeater Trustees Report}
Nothing to report.

\subsubsection{Field Day Committee Report}
Nothing to report.

\section{Old Business}
\begin{enumerate}
  \item \textbf{Board Members}
  \begin{enumerate}
    \item There were some irregularities in the formation of the ballot for December's officer and board voting. To address that, we decided to void the results of the previous month's voting. The club reverted back to the original board member list. Then, Dick (\texttt{W1REJ}) has offered to step down from the board, opening a seat. Greg (\texttt{WA1JXR}) was voted into the board.
    \item At the end of the December meeting (and start of the Janurary meeting) the board members were: \texttt{AB1MT}, \texttt{KC1BHD}, \texttt{W1TR}, \texttt{W4FEB}, \texttt{WA1JXR}, and \texttt{WW2JS}.
    \item At the end of the Janury business meeting (and the start of the January Board meeting) the board members were: \texttt{AB2IX}, \texttt{N1ZC}, \texttt{WA1JXR}, \texttt{W1TR}, \texttt{W4FEB}, and \texttt{WW2JS}.
  \end{enumerate}
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
\begin{enumerate}
  \item Alison Peters (\texttt{W1ABP}) became a CMARA member by majority vote. Welcome!
  \item Jeremy Peters (\texttt{W3SJP}) became a CMARA member by majority vote. Welcome!
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item Art (\texttt{WA1RCQ}) is looking for electricians who can help with some electrical issues around the church. The church has given us so much, so please consider helping if you're able.
  \item Bob (\texttt{KB1VUA}) is making a list of people interested in being a backup net control for George's Old Timer's Net. Please reach out to him if you're interested.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
No new hams nor hams with upgrades were present.

\subsection{Other News}
\begin{enumerate}
  \item A very well known CMARA member, Cisco (\texttt{W1JLC}), has become a silent key. Francisco (Cisco) Herrera was a huge help in starting the CMARA club. Please take a moment to remember the many good times and contacts had with him.
  \item It's time for the Boston Marathon again, and they're looking for volunteers. If you're interested, sign up at the marathon website, \texttt{http://www.baa.org}.
  \item John (\texttt{WW2JS}) is continuing to sell the custom made CMARA mugs. If you're interested in obtaining one, reach out to him.
\end{enumerate}

\section{Next Meeting}
The next meeting will be Thursday, February 16, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583. The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM.

\section{Meeting Adjourned}
The meeting was adjourned January 19, 2017 at 7:50 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
Terry (\texttt{W1TR}) gave a great presentation on SDR radio and contesting. Thanks, Terry!

\end{document}
