\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge March 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2017 board meeting was called to order on March 16, 2017 at 8:42 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No \\
  Greg Algieri      & \texttt{WA1JXR}   & No \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KC1GIB}

\subsection{Guests \& Visitors}
\texttt{KB2SAE},
Christopher Wentworth

\section{Primary Discussion}

\subsection{Unpaid Members}
\begin{enumerate}
\item According to the by-laws, we will publish the paid-up members in the March meeting minutes. The list of unpaid members will not be published.
\item Only the president and vice president (\texttt{KB1VUA} and \texttt{K1BML}) will reach out to people who are not caught up with dues. It can be a delicate situation and we don't want too many people to be involved.
\item Someone was nice enough to donate \$25.00 to the club to aid in the dues of someone that needs it. We thank you for the donation and thinking of the members.
\end{enumerate}

\subsection{Swap Meet Results}
\begin{enumerate}
\item The club held a swap meet during the March meeting and allowed members to swap goods at reasonable prices to others. We asked for a 5\% donation for cash sales (0\% for swaps) to help the club. The breakdown of the sales can be seen below.\\

\noindent
\begin{tabular}{|lllrr|r|}
\hline
    & \textbf{Item}             & \textbf{Seller Callsign} & \textbf{Sold For} & \textbf{Requested 5\%} & \textbf{Donated} \\ \hline \hline
\#1 & FL-2100B Amplifier        & Ray (\texttt{KM1D})      & \$200.00          & \$10.00                & \$10.00          \\ \hline
\#2 & Raspberry Pi / Misc       & Bob (\texttt{KB1VUA})    & \$60.00           & \$3.00                 & \$3.00           \\ \hline
\#3 & Heath SWR                 & Randy (\texttt{W4FEB})   & \$10.00           & \$0.50                 & \$0.50           \\ \hline
\#4 & Dual Band Ant. / 75M Ant. & John (\texttt{W1BFG})    & \$20.00           & \$1.00                 & \$1.00           \\ \hline
\#5 & \emph{Unknown}            & Tim (\texttt{W1AAM})     & \$60.00           & \$3.00                 & \$3.00           \\ \hline
\#6 & Modem                     & Sandy (\texttt{N1FSK})   & \$120.00          & \$6.00                 & \$6.00           \\ \hline
\#7 & Laptop                    & Jim (\texttt{KC1BHD})    & \$100.00          & \$5.00                 & \$5.00           \\ \hline \hline
    &                           &                          & \$570.00          & \$28.50                & \$28.50          \\ \hline
\end{tabular}\\

\item Adrian (\texttt{AB2IX}) raised his concerns about the organization during the swap meet and felt that we could likely do better next time with communication and keeping track of sales/swaps. Adrian shared that he would like to run the next swap meet.

\item We did miss quite a few swaps and potentially some sales. Because of this we don't have a complete record of what happened, and that would have been nice.

\item While some people gave away equipment for free and lowered costs, some people didn't use club-friendly pricing. We may want to have an emphasis on that next time.

\item One thing we may also benefit from is a formal start time. This month, sales and swaps were happening well before anyone was given any instructions or before anything was introduced. Perhaps next time we can have some early setup time for sellers and no sales are allowed until after the business meeting.

\item We are thankful for the \$28.50 that people donated to the club. Thank you all!
\end{enumerate}

\section{Next Month's Presentation}
Adrian (\texttt{AB2IX}) will be presenting ``Test Bench for Non-Technologist Hams: Part II''. The presentation will be about 45 minutes.

\section{Meeting Adjourned}
The meeting was adjourned March 16, 2017 at 8:56 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
