\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge July 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA July 2017 board meeting was called to order on July 20, 2017 at 7:05 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}). This board meeting was held at 102 Green St, Worcester, MA 01604 (The Hangover Pub).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & No \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & No \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KC1GIB}, \texttt{K1RAU}

\subsection{Guests \& Visitors}
Christopher Wentworth

\section{Primary Discussion}

\subsection{Field Day}
\subsubsection{Attendance}
We had 35 attendees, 10 of which were guests. All signed the needed waiver.

\newpage
\subsubsection{Points \& Score}

Terry (\texttt{W1TR}) provided us with our Field Day score, as shown below:

\noindent
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Band} & \textbf{Mode} & \textbf{QSO's} & \textbf{Points per QSO} & \textbf{Points} \\ \hline
3.5 & CW   & 252 & 2.0 & 504 \\ \hline
3.5 & LSB  & 57  & 1.0 & 57  \\ \hline
7   & CW   & 483 & 2.0 & 966 \\ \hline
7   & LSB  & 245 & 1.0 & 245 \\ \hline
14  & CW   & 255 & 2.0 & 510 \\ \hline
14  & PSK3 & 71  & 2.0 & 142 \\ \hline
14  & USB  & 1   & 1.0 & 1   \\ \hline
21  & CW   & 28  & 2.0 & 56  \\ \hline
21  & USB  & 33  & 1.0 & 33  \\ \hline
28  & USB  & 18  & 1.0 & 18  \\ \hline
\textbf{Total} & \textbf{All} & \textbf{1443} & \textbf{1.8} & \textbf{2532} \\ \hline
\end{tabular}\\

\noindent
We ended with a final score of 5,064. Good job everyone!

\subsubsection{Conditions of Site}
\begin{enumerate}
\item The site was very good this year, there were many trees to hang antennas from and the single entrance made it easy to guarantee people signed the waiver.
\item There were many ticks, but they were mostly dog ticks. That said, there weren't too many by the food tent.
\item The grounds were very well maintained, and we can thank Bob (\texttt{KB1VUA}) for that.
\end{enumerate}

\subsubsection{Food Service}
\begin{enumerate}
\item The food service at field day was an improvement over 2016. The food was simple and ready on demand.
\item The breakfast service on Sunday morning wasn't able to provide enough food for everyone, so that needs to be adjusted for.
\item Jim (\texttt{N1EKO}) reimbursed Mark (\texttt{W1IDE}) \$243.93 for the expenses of field day food.
\end{enumerate}

\section{Next Month's Presentation}
The next club meeting will be held on September 21, 2017. The meeting presentation will be an introduction to soldering by Greg (\texttt{WA1JXR}).

\section{Meeting Adjourned}
The meeting was adjourned July 20, 2017 at 7:23 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
