\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge October 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA October 2017 board meeting was called to order on October 19, 2017 at 8:26 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No  \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & No  \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KC1GIB}, \texttt{W1PA}

\subsection{Guests \& Visitors}
Christopher Wentworth

\section{Primary Discussion}

\subsection{Club QSL Cards}
\begin{enumerate}
  \item We are looking for someone to help send out QSL cards when needed. Right now it's done on an ad-hoc basis and it can be difficult to keep track of the files. We send out approximately three per year.
  \item Terry (\texttt{W1TR}) will send Mark (\texttt{W1IDE}) the QSL card images and Mark will price how much it would cost to print 100 of them. Printing them ahead of time (as opposed to by need) would reduce the work needed to fill them out.
\end{enumerate}

\subsection{Club Documents (Roster)}
\begin{enumerate}
  \item A discussion was had about moving some of the club documents into something like Google Drive, so a select group of people (officers) could modify and everyone could read. Mark (\texttt{W1IDE}) and Jim (\texttt{N1EKO}) will communicate to accomplish this.
\end{enumerate}

\subsection{State Registration}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) will check the status of the state registration and report back.
\end{enumerate}

\subsection{Swap Meet}
\begin{enumerate}
  \item Adrian (\texttt{AB2IX}) proposed having another swap meet at a club meeting.
  \item We'd be looking for the February / March time frame.
  \item We need to establish much better rules, as last time was a bit chaotic.
  \item We will likely have the meeting for club members only, with a specific purpose of helping other club members (lower prices).
  \item A discussion about putting items for sale in the monthly email, but that would be too much to maintain and could become too much like spam for some readers.
\end{enumerate}

\section{Next Month's Presentation}
\begin{enumerate}
  \item \textbf{Primary Plan:} Greg (\texttt{WA1JXR}) will check with Bruce about the presentation on the new FCC entry-level licenses.
  \item \textbf{Backup Plan:} Greg (\texttt{WA1JXR}) will be continuing with the soldering trainings and find a new video.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned October 19, 2017 at 8:48 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
