\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge April 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2017 business meeting was called to order on April 20, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:20 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No  \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No  \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA3RLZ},
\texttt{KB1VUA},
\texttt{KB1VXH},
\texttt{KB1VXY},
\texttt{KC1DYA},
\texttt{KC1FPI},
\texttt{KC1SGT},
\texttt{KG1GIB},
\texttt{KM1D},
\texttt{N1AZL},
\texttt{N1FF},
\texttt{N1FSK},
\texttt{N1HTB},
\texttt{N1JEL},
\texttt{N1KWX},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1DYQ},
\texttt{W1GD},
\texttt{W1IKE},
\texttt{W1JKS},
\texttt{W1PA},
\texttt{W1REJ},
\texttt{W1TR},
\texttt{W1WER},
\texttt{WA1MDD}
\texttt{WI1Y}

\subsection{Guests \& Visitors}
\texttt{AE1DX}*,
\texttt{KC1DMM},
\texttt{KC1GYT},
\texttt{KE8DHM},
\texttt{KW2T},
\texttt{N1AVP},
\texttt{N1TQ},
Ameena Jabbour,
Philip LaForest*\\

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
The secretary's report for March 2017 was voted in by voice vote.

\newpage
\subsection{Treasurer's Report}
The February and March 2017 Treasurer's report were voted in by voice vote.

\subsubsection{February 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,448.95} \\
  Income: Membership Dues & \texttt{+\$245.00} \\
  Income: Donations & \texttt{+\$20.00} \\
  Expenses: \emph{(None)} & \texttt{-\$0.00} \\
  Ending Checking Balance & \texttt{\$5,713.95} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$10,481.73} \\
  \hline
\end{tabular}

\subsubsection{March 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,713.95} \\
  Income: \emph{(None)} & \texttt{+\$0.00} \\
  Expenses: Member Badges & \texttt{-\$53.81} \\
  Ending Checking Balance & \texttt{\$5,660.14} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$10,427.92} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}

There is nothing new; Dick (\texttt{W1REJ}) does not have the latest figures.

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Greg (\texttt{WA1JXR}) warns of non-licensed people causing QRM (interference) on the \texttt{W1BIM} repeater. This is illegal, and the club suggestion on the matter is to ignore the individual(s) as they feed off the attention.
  \item The repeater is continuing to work fairly well.
  \item The trustees will be getting together soon to do a spring-time check of the repeater.
\end{enumerate}

\subsubsection{Field Day Committee Report}
The field day committee is going to meet after the presentation to discuss field day. Art (\texttt{WA1RCQ}) will sit in on the meeting.

\section{Old Business}
\begin{enumerate}
\item The February treasurer's report was voted in during the reports section of the meeting.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}

\begin{enumerate}
  \item Patrick (\texttt{AE1DX})
  \item George (\texttt{KB2SAE})
  \item Patrick (\emph{Not yet a ham.})
\end{enumerate}

All above were voted in by voice vote. Congratulations and welcome to CMARA.

\subsection{Other New Business}
There was no other new business.

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}

\begin{enumerate}
  \item Ameena Jabbour, got her technician and is awaiting the FCC to issue a callsign.
  \item Sandy (\texttt{N1FSK}) upgraded to extra.
  \item Nicole (\texttt{KE8DHM}) upgraded to general.
  \item Dean (\texttt{KC1FDQ}) upgraded to extra and got his vanity callsign (\texttt{W1DYQ}).
  \item Mike (\texttt{KC1GYT}) upgraded to extra.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
\item Greg (\texttt{WA1JXR}) reminds folks that the MCW project orders are due. If you're still interested in the project, reach out to Greg ASAP.
\item The FARA Flea Market is Sunday 4/23/17.
\item Deerfield is May 5 and 6.
\end{enumerate}

\section{Next Meeting}
The next meeting will be Thursday, May 18, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.\\

\noindent
The topic of the next meeting will be decided during the board meeting following the conclusion of the business meeting.

\section{Meeting Adjourned}
The meeting was adjourned April 20, 2017 at 7:45 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

Adrian (\texttt{AB2IX}) gave part two of his Ham Test Bench presentation. Thanks, Adrian!

\end{document}
