\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge January 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA January 2017 board meeting was called to order on January 19, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lynn Glagowski & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No  \\
  Greg Algieri      & \texttt{WA1JXR}   & No  \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

None

\subsection{Guests \& Visitors}

None

\section{Primary Discussion}

\subsection{Elections Process}
Bob (\texttt{KB1VUA}) proposed creating a by-law for the election process. This would avoid the mistakes of the months past.

\subsection{Repeater Committee Changes}
There is a proposed by-law change to require ten (10) CMARA members, in good standing, to approve change to the control of repeater committee.

\subsection{Future Presentations}
\begin{enumerate}
  \item Adrian (\texttt{AB2IX}) has a presentation for April. There is a question if this is firmly set or not.
  \item Terry (\texttt{W1TR}) has backup presentations if needed.
\end{enumerate}

\subsection{Meeting Times}
\begin{enumerate}
\item Bob (\texttt{KB1VUA}) would like to change the board meetings to 30 minutes before the regular business meeting.
\item There was an proposal to have a couple of board meetings a year at a central location in addition to the regular meetings. We could use teleconferencing (Like Google Hangouts or the alike).
\item Bob (\texttt{KB1VUA}) and Brian (\texttt{K1BML}) will be at the meeting at 6:30 PM.
\item We need to let members know that social time will begin at 6:30 PM and the meeting will follow at 7:00.
\end{enumerate}

\subsection{Non-Profit Status}
We need to straighten out our non-profit status. We'd like to be 501(c)(3) for the benefits.

\subsection{Field Day}
\begin{enumerate}
  \item We need to begin to work on our field day communications. Mark (\texttt{W1IDE}) has means of communicating with the club, and will be a resource for that.
  \item Adrian (\texttt{AB2IX}) has volunteered to follow the weather three weeks before and up to field day.
\end{enumerate}

\section{Next Month's Presentation}
Sandy (\texttt{N1FSK}) will give a presentation on CMARA history for the next meeting (February).

\section{Meeting Adjourned}
The meeting was adjourned January 19, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
