\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge March 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2017 business meeting was called to order on March 16, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:17 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{K1ALN},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA1SPY},
\texttt{KB1VXH},
\texttt{KB1VXY},
\texttt{KC1ACX},
\texttt{KC1BHD},
\texttt{KC1ETB},
\texttt{KC1FPI},
\texttt{KC1GIB},
\texttt{KM1D},
\texttt{N1FSK},
\texttt{NE1R},
\texttt{W1AHM},
\texttt{W1BFG},
\texttt{W1CAB},
\texttt{W1GJM},
\texttt{W1IDE},
\texttt{W1REJ},
\texttt{W1WER},
\texttt{WA1MDD},
\texttt{WA1RCQ},
\texttt{WI1Y}

\subsection{Guests \& Visitors}
\texttt{AB1HT},
\texttt{AE1DX},
\texttt{KA1AQP},
\texttt{KA3RLZ},
\texttt{KB2SAE},
\texttt{KC1BCY},
\texttt{KC1SGT},
\texttt{KW2T},
\texttt{N1FF},
\texttt{N1JEL},
\texttt{W1AAM},
Christopher Wentworth

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
The secretary's report for February 2017 was voted in by voice vote.

\newpage
\subsection{Treasurer's Report}
The treasurers report for February will be tabled until the April meeting.

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
Nothing to report. We did have several new visitors present at the February meeting.

\subsubsection{Repeater Trustees Report}
Nothing to report. No communications have been made with Kurt, as the trustees are waiting for the better weather.

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report, as the head of the committee was not present.
  \item The Astronomy Club (Aldrich Astronomical Society, Inc.) has given the okay for us to use their field this year. Just like last year, the field will only be open to CMARA members in good standing, and not to the public. Bob (\texttt{KB1VUA}) is on the board of the Aldrich Astronomical Society, and the club members would be guests of his.
  \item There have been many improvements to the field, such as the completion of the building and there will be hot water this year to assist with proper cooking crew hand and utensil washing during the event.
  \item We will likely still have a liability waiver that people will need to sign upon entry. This will be enforced better than last year, and we will likely have a table at the entrance to ensure everyone signs.
  \item Brian (\texttt{K1BML}) will be the safety officer again this year.
\end{enumerate}

\section{Old Business}
There was no business tabled from February.

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}

Without the treasurer present, no new members were voted in. All business pertaining to membership will be tabled until April.

\subsection{Other New Business}
\begin{enumerate}
  \item Last month, Mark (\texttt{W1IDE}) shared with the club that he open-sourced many documents and templates on GitHub. Upon discussions with the other officers, it was decided that there is value in having all club resources under the \texttt{cmara.org} domain. For this reason, the GitHub page and all associated assets have been taken offline.

  \newpage
  \item According to the by-laws, we must publish the list of paid-up members.
  \begin{enumerate}
  \item By-Laws Excerpt:
    \begin{tcolorbox}
Section 4 - In the March bulletin and/or meeting minutes a roster of paid-up members shall be published. At the April Board of Directors meeting, the Treasurer shall submit a list of all members in arrears on dues. The names of all members in arrears shall be removed from all rosters and mailing lists and their membership privileges suspended.
  \end{tcolorbox}
  \item At the start of the March meeting, we had 63 paid-up members, and they are below. \\
  \begin{tabular}{|ll||ll|}
  \hline
  \textbf{Callsign} & \textbf{Name} & \textbf{Callsign} & \textbf{Name} \\
  \hline
  \texttt{AA2S}   & Bill Michalson      & \texttt{N1FSK}  & Sandy Lancraft      \\
  \texttt{AB1MT}  & George Szarka       & \texttt{N1HTB}  & Dimitris Paliyannis \\
  \texttt{AB1ZW}  & Marc Abretti        & \texttt{N1KWX}  & Hugh Bouchard       \\
  \texttt{K1ALN}  & Alan Ruuska         & \texttt{N1TYH}  & Steven Olivieri     \\
  \texttt{K1BML}  & Brian Loverro       & \texttt{N2LND}  & John Barbato        \\
  \texttt{K1QJM}  & Achille A. Levesque & \texttt{N9PVF}  & David Lipson        \\
  \texttt{K1RAU}  & Dan Rau             & \texttt{NE1R}   & Thomas C. Carrigan  \\
  \texttt{K1YYT}  & Gerard Bachand      & \texttt{W1ABP}  & Alison Peters       \\
  \texttt{KA1SPY} & John Kenney         & \texttt{W1AHM}  & Alan H. Martin      \\
  \texttt{KA2CNN} & Dwight Ernest       & \texttt{W1BFG}  & John Boyd           \\
  \texttt{KB1EZF} & Scott Olsen         & \texttt{W1BGL}  & Nicholas Gatzios    \\
  \texttt{KB1LOU} & Ron DiProfio        & \texttt{W1BNC}  & Mike Keller         \\
  \texttt{KB1NIQ} & Michelle Martin     & \texttt{W1CAB}  & Craig Bolen         \\
  \texttt{KB1OQA} & Thomas Turner       & \texttt{W1DYQ}  & Dean  Huggins       \\
  \texttt{KB1QZD} & Clovis Padilha      & \texttt{W1GD}   & Gerald  Kersus      \\
  \texttt{KB1VUA} & Robert Peloquin Jr  & \texttt{W1GJM}  & Gary McMeekin       \\
  \texttt{KB1VXH} & George Saari        & \texttt{W1IDE}  & Mark Ide Jr         \\
  \texttt{KB1VXY} & John J. Iwuc        & \texttt{W1IKE}  & Roger Ikonan        \\
  \texttt{KC1ACX} & Vernie Grady        & \texttt{W1PA}   & Bill Acito          \\
  \texttt{KC1BHD} & James Garner        & \texttt{W1REJ}  & Richard Jubinville  \\
  \texttt{KC1BKW} & Michael DesChenes   & \texttt{W1RJZ}  & Ralph Zottola       \\
  \texttt{KC1DQT} & Robert Diehl        & \texttt{W1RVY}  & Eric  Wilhelm       \\
  \texttt{KC1DTT} & Michael Latour      & \texttt{W1WER}  & James A. Young      \\
  \texttt{KC1DYA} & Kevin Romines       & \texttt{W3DEC}  & Don Carlton         \\
  \texttt{KC1ETB} & Craig Brauckmiller  & \texttt{W3SJP}  & Jeremy Peters       \\
  \texttt{KC1FPI} & Maurice Quirke      & \texttt{W4FEB}  & Randolph Dore       \\
  \texttt{KC1GBK} & Jamie Giampietro    & \texttt{WA1JXR} & L. Greg Algieri     \\
  \texttt{KC1GIB} & Herbert Gilbert     & \texttt{WA1MDD} & John Spencer        \\
  \texttt{KC1SGT} & Joe Rich            & \texttt{WA1RCQ} & Arthur B. Kass      \\
  \texttt{KM1D}   & Ray Donadt          & \texttt{WI1Y}   & Mickey Westover     \\
  \texttt{N1AVP}  & Morris Beverly      & \texttt{WW2JS}  & Jonathan Sherman    \\
  \texttt{N1EKO}  & James Singer        &                 &                     \\
  \hline
  \end{tabular}

  \item During the April board meeting, discussions will be had about members who have not paid their 2017 dues. It's important to note that no action has been taken yet, so if you're not on the list it's not to late. Reach out to the club ASAP.

  \item Only the president and vice president will be in contact with members who are not caught up.

  \item Some folks paid (or tried to pay) during the March meeting. These renewals have not yet been processed by the treasurer. Please check in with him for more information.

\end{enumerate}
  \newpage
  \item Greg (\texttt{WA1JXR}) provided the club with an update for the MCW (Modulated CW) project. If you're interested in taking part of the project, email Greg at \texttt{wa1jxr@comcast.net}. Greg shared a prototype of the board, with all soldering and wires attached. The cost for the project will be \$50.00 for the complete kit, but you will still need a CW key and various cables depending on your setup. If all goes well, the kits could be ready for the April meeting.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}

No new hams present nor upgrades this month.

\subsection{Other News}
\begin{enumerate}
\item There are many upcoming hamfests. Some are listed below, taken from \texttt{W1GSL}'s list which is usually up to date. Visit \texttt{http://web.mit.edu/w1gsl/Public/ne-fleas} for more info.

\begin{tcolorbox}
\begin{verbatim}
New England Area   Ham - Electronic Flea Market  ***  DATES ***   2017 P 1 of 2
*******************************************************************************
2017                                                    Contact          Source
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
19 Mar Southington CT SARA @HS $5@8 $20/T@6:15      John WA1JKR 860 621 8791 W+

19 Mar Henniker NH CVRC @CommSch                 Jeffrey KB1WTI 603 831 9352  +

31 Mar - 1 Ap Lewiston ME AARC ME Conv @Ramada @8    Ivan N1OXA 207 784 0350 W

8 Ap Newton MA PHSNE Photographica Sat Only @AmLegion @9A  John 781 592 2553

8 Ap Hampton NH PCARC @Masonic  $5@8 $10/T@7          Mark K1RX 603 775 0220 F

8 Apr LaSalle PQ MARC @RC Legion $5@9 $10/T@8:15      Jim VE2VE 514-990-1965 R

8 Apr Windsor CT VR+C Mus 115 Pierson LN @8AM Indoor       John 860 673 0518  +

15 April S Portland ME PAWA @AmLegion               Bryce K1GAX 207 415 0498 A

16 Apr Cambridge MA             Flea at  MIT              Mitch 617 253 3776 F
                      Third Sunday April thru October

... [SNIP] ...

*******************************************************************************
LAST UPDATE 3-14-17 de W1GSL         http://swapfest.us                    P 1
List is normally updated twice a month - look for the latest version
*******************************************************************************
Additions/ Corrections via e-Mail   w1gsl@mit.edu  <- SUBSCRIBE
US Mail  W1GSL POB 397082 MIT Br Cambridge MA 02139
(c)2017 W1GSL unlimited reproduction permitted in entirety
\end{verbatim}
\end{tcolorbox}

\item James Young (\texttt{W1WER}) attended the meeting and was recognized for being a past president of CMARA. Thank you for your continued support, Jim!
\end{enumerate}

\section{Next Meeting}
The next meeting will be Thursday, April 20, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.\\

\noindent
The topic of the next meeting will be decided during the board meeting following the conclusion of the business meeting.

\section{Meeting Adjourned}
The meeting was adjourned March 16, 2017 at 7:50 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

We had a swap meet during the March meeting and it went very well. The results and metrics of the swap will be discussed during the board meeting tonight.

\end{document}
