\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge April 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA April 2017 board meeting was called to order on April 20, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KC1GIB}

\subsection{Guests \& Visitors}
Christopher Wentworth

\section{Primary Discussion}

\subsection{Club Projector}
Bob (\texttt{KB1VUA}) brought up the need for the club to purchase a new projector for the presentations. The old one is just not up to the task anymore. The board voted to spend no more than \$600.00 on a new projector. We will try to sell the old projector to members first, then the general public. Voted in by voice vote, all in agreement.

\subsection{Field Day}
\begin{enumerate}
  \item We are going to try to get new members to help out during field day.
  \item We are going to look at easier options for field day foods. It is felt that we can cut down the time cooking and preparing.
  \item Weather permitting, we'd like to have telescope observing at the field on Saturday night. When we set up for this we don't want white lights (flashlights or headlights) shining in our eyes because it takes about half an hour to recover from being blinded by white light. If we are observing we will request that all super-bright flashlights be turned off and no cars will be allowed in or out with headlights lit so we may open up the observatory and set up another scope outside as well. The use of red flashlights will be required from dark utill we close up the observatory for the night.
  \item We will work with Gerry (\texttt{W1GD}) to get a group formed specifically to assemble the antennas.
\end{enumerate}

\subsection{Unpaid Members}
Bob (\texttt{KB1VUA}) and Brian (\texttt{K1BML}) went through the list of unpaid members.

\subsection{Radio Donation Sales}
We can now roll the ``Radio Donation Sales'' funds into the ``General Fund''. We need to let Jim (\texttt{N1EKO}) know.

\subsection{ARRL Listing}
Greg (\texttt{WA1JXR}) updated the CMARA listing on ARRL.

\section{Next Month's Presentation}
Next month's presentation will be an open discussion on Field Day planning.

\section{Meeting Adjourned}
The meeting was adjourned April 20, 2017 at 9:49 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
