\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge December 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA December 2017 business meeting was called to order on December 21, 2017 at 7:03 PM by CMARA vice president Brian Loverro (\texttt{K1BML}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & No  \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & Yes \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AB2IX},
\texttt{K1RAU},
\texttt{KA3RLZ},
\texttt{KB1LOU},
\texttt{KB1VXY},
\texttt{KC1FPI},
\texttt{KC1GIB},
\texttt{KC1SGT},
\texttt{N1FF},
\texttt{N1FSK},
\texttt{N1HTB},
\texttt{W1CAB},
\texttt{W1PA},
\texttt{W1WER},
\texttt{WA1MDD},
\texttt{WA1RCQ},
Bruce de Graaf

\subsection{Guests \& Visitors}
\texttt{K1TIN},
\texttt{KC1IQN},
\texttt{KC1SGT},
Christopher Wentworth

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item The November secretary's report was approved by voice vote.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item The November treasurer's report was approved by voice vote.
\end{enumerate}

\subsubsection{October 2017 Treasurer's Summary}
\noindent
\emph{Pending getting November summary.}
% \begin{tabular}{|l|r|}
%   \hline
%   Beginning Checking Balance & \texttt{\$5,080.50} \\
%   Income: Deposit & \texttt{+\$611.00} \\
%   Expense: Equipment & \texttt{-\$169.95} \\
%   Expense: Liability Insurance & \texttt{-\$200.00} \\
%   Expense: Membership Badges & \texttt{-\$50.81} \\
%   Ending Checking Balance & \texttt{\$5,270.74} \\
%   \hline
%   \hline
%   CD & \texttt{\$4,767.78} \\
%   \hline
%   \hline
%   Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
%   \hline
%   \hline
%   \textbf{Total Club Account} & \texttt{\$10,038.52} \\
%   \hline
% \end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\section{Old Business}
\begin{enumerate}
  \item No old business.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA!
\begin{enumerate}
  \item Dan Pedtke (\texttt{KW2T}) was voted in as our newest member. Welcome to CMARA!
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item Herb (\texttt{KC1GIB}) let the club know that he would be unable to run for the position of treasurer due to a recent passing in his family. Please keep Herb in your thoughts in prayers during this difficult time.
  \item Lyn (\texttt{WB1CCL}) requested permission to renew the \texttt{www.cmara.org} and similar websites. This motion was approved by voice vote and she will let the club know the bill.
  \item Jim (\texttt{N1EKO}) mentioned that our CD will be maturing in a few days. There was a motion on the floor to let it roll over for another 12-month cycle so we can decide what to do with it. The motion was approved by voice vote.
  \item Jim (\texttt{N1EKO}) will not be returning to work as expected and will run as a write-in for treasurer.
  \item Alan (\texttt{W1AHM}) shared that the ARRL New England Division director will be having a cabinet meeting on January 6th. This is a good opportunity for us to send a representative from the club to bend the ARRL's ear so they know what we desire.
  \item The elections, while technically new business, will be held at the end of the meeting.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item Bruce de Graaf \emph{(no call yet)} is a new ham. Welcome to the hobby, Bruce!
  \item Mike Selent (\texttt{KC1IQN}) is also a new ham. Welcome to the hobby, Mike!
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item Morris (\texttt{KC1FPI}) brought up how much it would mean to Herb (\texttt{KC1GIB}) to have people reach out during this difficult time for him. Herb lost his brother very recently, and would love to hear from people.
  \item It's Adrian (\texttt{AB2IX})'s final day at work tomorrow, as he's retiring. We'd like to congratulate Adrian in the many years he's dedicated to engineering and hope he enjoys retirement.
  \item Also, Mike (\texttt{W1BNC}) recently retired from his position, so we'd like to congratulate him on his many years dedicated to broadcast. We all wish you the best, Mike!
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, December 21, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item The next meeting's presentation will be a Skype presentation from Bob Naumann (\texttt{W5OV}) on the DX Engineering Story.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned December 21, 2017 at 7:43 PM by CMARA vice president Brian Loverro (\texttt{K1BML}).

\section{Post-Meeting Presentation}
This month was our annual elections and potluck. Thank you to everyone for participating.

\newpage
\section{Elections}

A total of forty (40) people participated in the voting of officers and the board this year. Thirty-Seven (37) of them were in-person during the meeting and three (3) of them submitted absentee ballots to Mark Ide (\texttt{W1IDE}) prior to the meeting.

\begin{enumerate}
  \item Office of President

  \begin{tabular}{|p{1in}|p{.75in}|p{.6in}|p{1.2in}|p{.75in}|p{.75in}|}
  \hline
  \textbf{Votes}       & \textbf{Votes}      & \textbf{Total} & \textbf{Name} & \textbf{Callsign} & \textbf{Election} \\
  \textbf{(In Person)} & \textbf{(Absentee)} & \textbf{Votes} &               &                   & \textbf{Status}   \\ \hline
  37 Votes & 3 Votes & 40 Votes & Robert Peloquin Jr. & \texttt{KB1VUA} & Elected \\ \hline
  \end{tabular}

  \item Office of Vice President

  \begin{tabular}{|p{1in}|p{.75in}|p{.6in}|p{1.2in}|p{.75in}|p{.75in}|}
  \hline
  \textbf{Votes}       & \textbf{Votes}      & \textbf{Total} & \textbf{Name} & \textbf{Callsign} & \textbf{Election} \\
  \textbf{(In Person)} & \textbf{(Absentee)} & \textbf{Votes} &               &                   & \textbf{Status}   \\ \hline
  37 Votes & 3 Votes & 40 Votes & Brian Loverro & \texttt{K1BML} & Elected \\ \hline
  \end{tabular}

  \item Office of Secretary

  \begin{tabular}{|p{1in}|p{.75in}|p{.6in}|p{1.2in}|p{.75in}|p{.75in}|}
  \hline
  \textbf{Votes}       & \textbf{Votes}      & \textbf{Total} & \textbf{Name} & \textbf{Callsign} & \textbf{Election} \\
  \textbf{(In Person)} & \textbf{(Absentee)} & \textbf{Votes} &               &                   & \textbf{Status}   \\ \hline
  37 Votes & 3 Votes & 40 Votes & Mark Ide Jr. & \texttt{W1IDE} & Elected \\ \hline
  \end{tabular}

  \item Office of Treasurer

  \begin{tabular}{|p{1in}|p{.75in}|p{.6in}|p{1.2in}|p{.75in}|p{.75in}|}
  \hline
  \textbf{Votes}       & \textbf{Votes}      & \textbf{Total} & \textbf{Name} & \textbf{Callsign} & \textbf{Election} \\
  \textbf{(In Person)} & \textbf{(Absentee)} & \textbf{Votes} &               &                   & \textbf{Status}   \\ \hline
  0 Votes & 0 Votes & 0 Votes & Herbert Gilbert & \texttt{KC1GIB} & \emph{Withdrew} \textasteriskcentered{} \\ \hline
  20 Votes & 0 Votes & 20 Votes & James Singer & \texttt{N1EKO} & \emph{Withdrew} \textasteriskcentered{} \\ \hline
  17 Votes & 2 Votes & 19 Votes & Randolph Dore & \texttt{W4FEB} & Elected \\ \hline
  0 Votes & 1 Vote & 1 Vote & \emph{(Blank)} &  &  \\ \hline
  \end{tabular}

  \textasteriskcentered{} Please see the board meeting minutes for a complete description into the election for treasurer. This is just a summary of the outcome.

  \item Office of Webmaster

  \begin{tabular}{|p{1in}|p{.75in}|p{.6in}|p{1.2in}|p{.75in}|p{.75in}|}
  \hline
  \textbf{Votes}       & \textbf{Votes}      & \textbf{Total} & \textbf{Name} & \textbf{Callsign} & \textbf{Election} \\
  \textbf{(In Person)} & \textbf{(Absentee)} & \textbf{Votes} &               &                   & \textbf{Status}   \\ \hline
  37 Votes & 3 Votes & 40 Votes & Linda Glagowski & \texttt{WB1CCL} & Elected \\ \hline
  \end{tabular}

  \item Board of Directors

  \begin{tabular}{|p{1in}|p{.75in}|p{.6in}|p{1.2in}|p{.75in}|p{.75in}|}
  \hline
  \textbf{Votes}       & \textbf{Votes}      & \textbf{Total} & \textbf{Name} & \textbf{Callsign} & \textbf{Election} \\
  \textbf{(In Person)} & \textbf{(Absentee)} & \textbf{Votes} &               &                   & \textbf{Status}   \\ \hline
  37 Votes & 3 Votes & 40 Votes & Adrian Zeffert & \texttt{AB2IX} & Elected \\ \hline
  37 Votes & 3 Votes & 40 Votes & George Gumbrell & \texttt{KA3RLZ} & Elected \\ \hline
  37 Votes & 3 Votes & 40 Votes & L. Greg Algieri & \texttt{WA1JXR} & Elected \\ \hline
  37 Votes & 3 Votes & 40 Votes & Terry Glagowski & \texttt{W1TR} & Elected \\ \hline
  37 Votes & 3 Votes & 40 Votes & Dan Rau & \texttt{K1RAU} & Elected \\ \hline
  33 Votes & 3 Votes & 36 Votes & Scott Olsen & \texttt{KB1EZF} & Elected \\ \hline
  4 Votes & 0 Votes & 4 Votes & \emph{(Blank)} & & \\ \hline
  \end{tabular}
\end{enumerate}

\end{document}
