\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge June 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA June 2017 board meeting was called to order on June 15, 2017 at 9:30 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & No \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KC1GIB}, \texttt{AE1DX}

\subsection{Guests \& Visitors}
Christopher Wentworth

\section{Primary Discussion}

\subsection{Field Day}
\begin{enumerate}
  \item People will want to bring chairs for field day, many of us will be there for long hours and it's something that's easily forgotten.
  \item Brian (\texttt{K1BML}) will be lending the club some hand-held radios for use during field day to reach him in the case of emergency.
  \item Mark (\texttt{W1IDE}) will send out the field day survey.
  \item There was a discussion during the business meeting regarding cold cuts (sandwiches) and their potential during field day. From the sounds of it, we'll want to do hot meals.
  \item We'll want to remind members to bring their own snacks and coolers with drinks. Also it's important to realize that drinks should be cooled ahead of field day so they're cold for field day.
  \item We need to work out the exact details of the network for field day, Bob (\texttt{KB1VUA}) will work with Jim (\texttt{KC1BHD}) tomorrow.
  \item We still need to figure out the power situation, we need quiet generators (both RF noise and audible noise).
  \item We will have a big generator by the food tent.
  \item We need people to bring extension cords.
  \item Adrian (\texttt{AB2IX}) will have a station with cell phone and HT chargers.
  \item We need to have a scheduled food time, to prevent a rush like last year. We may have someone walk to inform when it's their turn.
  \item For lunch, we'll likely do burgers and hot dogs.
  \item We will have 15 gallons of spare gas, from Bob (\texttt{KB1VUA}).
  \item Terry (\texttt{W1TR}) will bring his bow and arrow.
  \item If clear and the observatory is open, red lights will be required as to not ruin everyone's light sensitivity.
  \item If you do not have a red flashlight, you can get one on eBay, or go to an auto store and get tail-light repair tape.
  \item Mark (\texttt{W1IDE}) to send the liability waiver.
  \item Saturday night will be a group meal.
  \item Everyone will be responsible for their own allergies.
\end{enumerate}

\section{Next Month's Presentation}
The next meeting will be after field day, and the content will be decided at the July board meeting.

\section{Meeting Adjourned}
The meeting was adjourned June 15, 2017 at 10:00 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
