\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge December 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA December 2017 board meeting was called to order on December 21, 2017 at 8:40 PM by CMARA vice president Brian Loverro (\texttt{K1BML}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & No  \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\emph{(None)}

\subsection{Guests \& Visitors}
\emph{(None)}

\section{Primary Discussion}

\subsection{Treasurer}
\begin{enumerate}
  \item There were some concerns about the way the election was performed for the position of treasurer. There were a series of events that played out as follow:
  \begin{enumerate}
    \item Jim (\texttt{N1EKO}) said he wouldn't `run away' from the position, but wouldn't be running. This was done in the October meeting.
    \item Herb (\texttt{KC1GIB}) was nominated to run for treasurer. This was done in the October meeting.
    \item Randy (\texttt{W4FEB}) was nominated to run for treasurer. This was done in the November meeting.
    \item Herb (\texttt{KC1GIB}) withdrew his nomination as he experienced a family passing and wouldn't be able to fulfill the position. This was announced to the club in an email prior to the December meeting and again during the business portion of the December meeting.
    \item During the December business meeting, Jim (\texttt{N1EKO}) announced that he wouldn't be returning back to work as expected, so he would run as a write-in. There were comments made about Randy (\texttt{W4FEB}) potentially not desiring the position. At this time, none of the other candidates were asked for a response, and without any concerns being immediately raised, we moved on fairly quickly.
    \item The elections began, and Mark (\texttt{W1IDE}) asked all questions to be raised before the elections were to begin, as it's always much harder to remedy situations after the ballots are cast. There were no comments or concerns at this point.
    \item The elections occurred, and the winner was Jim (\texttt{N1EKO}) by a very small margin. There was one member who wrote a `?' symbol in the write in, and upon discussion with that individual, they simply didn't know Jim's name, so we counted that in Jim's favor. That one vote broke the tie and made Jim (\texttt{N1EKO}) the treasurer.
    \item After the winners were announced, Randy (\texttt{W4FEB}) contested the ballot, with several valid concerns. Namely that the absentee ballots were not given a fair opportunity to vote for Jim (\texttt{N1EKO}) and that he (Randy) wasn't given sufficient time to describe his desire to run.
    \item The 2017 board was called for a meeting and we discussed the outcomes.
  \end{enumerate}
  \item The 2017 board of directors held a meeting and covered the following points:
  \begin{enumerate}
    \item Randy (\texttt{W4FEB}) felt he was not given sufficient time to respond to the false statements about him not wanting the position. More than half of the board agreed.
    \item John (\texttt{WW2JS}) raised concern about the club breaking several state and federal laws with the way we conducted the election, by not giving Randy (\texttt{W4FEB}) sufficient time to talk.
    \item Upon discussion, it came to light that Jim (\texttt{N1EKO}) didn't wish to hold the position, and Randy (\texttt{W4FEB}) did wish to.
    \item It was proposed that Jim (\texttt{N1EKO}) withdraw from the position, leaving Randy (\texttt{W4FEB}) the winner. Jim (\texttt{N1EKO}) agreed and Randy (\texttt{W4FEB}) became the 2018 treasurer.
  \end{enumerate}
  \item We learned several lessons that will need to be investigated for action items, and potentially update our by-laws.
  \begin{enumerate}
    \item What happens if there is a tie for a position?
    \item What happens if we need to reissue the ballots? Is it just for the position in question, or all of them? What about absentee ballots?
    \item Should there be a requirement to ask each candidate for a response or final comment prior to ballots being issued?
  \end{enumerate}
\end{enumerate}

\subsection{CMARA Website}
\begin{enumerate}
  \item Adrian (\texttt{AB2IX}) raised concern about the outdated state of the \texttt{www.cmara.org} website.
  \item Terry (\texttt{W1TR}) informed the board that while Lyn (\texttt{WB1CCL}) is the webmaster, she is not the content provider.
  \item If we need to update the website, we should send Lyn (\texttt{WB1CCL}) and Terry (\texttt{W1TR}) the changes and they'll get published.
\end{enumerate}

\section{Next Month's Presentation}
The next meeting is January 18th, 2018. We'll have a remote (Skype) presentation from Bob Naumann (\texttt{W5OV}).  He will be presenting the DX Engineering Story.

\section{Meeting Adjourned}
The meeting was adjourned December 21, 2017 at 8:45 PM by CMARA vice president Brian Loverro (\texttt{K1BML}).

\end{document}
