\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge May 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA May 2017 business meeting was called to order on May 18, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:07 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}

\texttt{AE1DX},
\texttt{K1RAU},
\texttt{KA1AQP},
\texttt{KA3RLZ},
\texttt{KC1BHD},
\texttt{KC1ETB},
\texttt{KM1D},
\texttt{N1AZL},
\texttt{N1HTB},
\texttt{N1KWX},
\texttt{N1TQ},
\texttt{W1CAB},
\texttt{W1GD},
\texttt{W1PA},
\texttt{W1REJ},
\texttt{WA1RCQ},
\texttt{WI1Y}

\subsection{Guests \& Visitors}
\texttt{K1GRE},
\texttt{KC1HOZ}*,
\texttt{KE8DHM},
Philip LaForest

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
The secretary's report for April 2017 was voted in by voice vote.

\newpage
\subsection{Treasurer's Report}
The April 2017 Treasurer's report was read by Mark (\texttt{W1IDE}) (as the treasurer was absent) and was voted in by voice vote.

\subsubsection{April 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,660.14} \\
  Income: Membership Dues & \texttt{+\$392.00} \\
  Income: Donations & \texttt{+\$20.00} \\
  Expenses: Membership Badges & \texttt{\$18.94} \\
  Expenses: Membership Badges & \texttt{\$134.00} \\
  Ending Checking Balance & \texttt{\$5,899.20} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$10,666.98} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item We are continuing to get new members.
  \item We need to give Dick (\texttt{W1REJ}) the current list of members. Jim (\texttt{N1EKO}) will be a good source for this.
  \item Some people are doing illegal things on the \texttt{W1BIM} repeater. It's important to remind the membership of the legal ramifications of transmitting illegally. People are playing music and advertising. Someone in Maine just got fined \$14,000 for illegal transmissions.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item There is nothing new to report.
  \item Spring testing still needs to be done, they're looking for a date that will work for all people involved.
\end{enumerate}

\subsubsection{Field Day Committee Report}
Tonight's presentation will be on field day planning, including a presentation about our performance last year.

\section{Old Business}
There was no old business tabled.

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}

Selina (\texttt{KC1HOZ}) voted in by voice vote. Congratulations and welcome to CMARA.

\subsection{Other New Business}
\begin{enumerate}
  \item The new projector will be used for the first time during this meeting.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item Selina (\texttt{KC1HOZ}) is a new ham.
  \item Joseph (\texttt{K1GRE}) upgraded to general.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item Dick (\texttt{W1REJ}) will bring refreshments to the June meeting.
  \item John (\texttt{WW2JS}) has created is own club and is accepting donations if you would like help putting an antenna up.
  \item We would like to thank Adrian (\texttt{AB2IX}) for last month's presentation.
  \item The Modulated-CW project's parts have been ordered, and have arrived. Greg (\texttt{WA1JXR}) will be looking at them shortly. The circuit boards are on order and by the next meeting should be in. There is no enclosure yet. There were 28 people that signed up.
  \item The Twin State Radio Club (\texttt{W1FN}) visited our club tonight. For details on their offerings, please visit their website \texttt{www.w1fn.org}.
\end{enumerate}

\section{Next Meeting}
The next meeting will be Thursday, June 15, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.\\

\noindent
The topic of the next meeting will be the 2017 field day. Please bring your laptops if you plan on setting up a station at field day. We need to verify \texttt{N1MM+} setups.

\section{Meeting Adjourned}
The meeting was adjourned May 18, 2017 at 7:28 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}

\begin{enumerate}
  \item Field Day 2016 Wrap-Up
  \begin{enumerate}
    \item Field day 2016 was a large success, we have 26 members show, 19 of which operated.
    \item There were no serious failures.
    \item Brian (\texttt{K1BML}) was the safety officer.
    \item 2016 was hotter than 2015, but at least we didn't have the rain.
    \item We finished 10th in 6A, we could have been 5A, but we wanted to leave an opportunity for people to get on the air.
    \item We had the following QSO's:\\
    \begin{tabular}{|l|l|}
    \hline
    CW      & 1108 \\ \hline
    Digital & 25   \\ \hline
    Phone   & 471  \\ \hline \hline
    Total   & 1604 \\ \hline
    \end{tabular}
    \item There were a handful of issues we had last year.
    \begin{enumerate}
      \item There was a time when there were two stations on 75-meters phone at the same time, but thankfully didn't transmit at the same time.
      \item There were some network issues, but they were ironed out after some time.
      \item We need someone to manage power, last year we didn't know who ran what generators, or who was manning the solar powers.
      \item We could use better scheduling of stations. CW was well stacked, but we lacked phone operators.
      \item We couldn't get 100\% of people to operate.
      \item The generators were making noise on low frequencies.
      \item Station computer passwords: if someone goes to get food or go to sleep, their computer may lock, making the station useless. It's proposed to shut passwords off.
      \item There was one potential medical emergency due to the heat. After some rest, the member was fine.
      \item The food service was overwhelmed by demand. We need to have a food manger to plan meals and schedule.
    \end{enumerate}
  \end{enumerate}
    \item The plan is to operate at Aldrich Astronomical Society again.
    \item We have the following coordinators / managers:\\
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Position} & \textbf{Person} \\ \hline
    Site Coordinator & Bob (\texttt{KB1VUA}) \\ \hline
    Field Day Chairman & Gerry (\texttt{W1GD}) \\ \hline
    Safety Officer & Brian (\texttt{K1BML}) \\ \hline
    Food Officer & Mark (\texttt{W1IDE}) \\ \hline
    Logging & Terry (\texttt{W1TR}) via \texttt{N1MM+} \\ \hline
    Power & \emph{To be determined.} \\ \hline
    Networking & Jim (\texttt{KC1BHD}) \\ \hline
    \end{tabular}
    \item We'll operate at 6A again as it offers the most flexibility.
    \item On Friday night we'll have camping open, and maybe even a fire going.
    \item This will not be open to the public, just like last year.
    \item We will try to make a press release.
    \item There will be a public info table at the entrance.
    \item We are going to try for educational points.
    \item We will try to get an elected government official to attend.
    \item Bob will look into the porta-potty.
    \item After dark all flashlights need to be red and headlights will need to be avoided. There are military lights with red attachments on ebay.
\end{enumerate}

\end{document}
