\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge November 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA November 2017 business meeting was called to order on November 16, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:00 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & No  \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & No  \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AB1ZW},
\texttt{AC1CO},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA1SPY},
\texttt{KA3RLZ},
\texttt{KB1EZF},
\texttt{KB1VXY},
\texttt{KB1YLA},
\texttt{KC1DMM},
\texttt{KC1DYA},
\texttt{KC1ETB},
\texttt{KC1GIB},
\texttt{KM1D},
\texttt{N1FF},
\texttt{N1HTB},
\texttt{N1KWX},
\texttt{W1AHM},
\texttt{W1BFG},
\texttt{W1CAB},
\texttt{W1DYQ},
\texttt{W1PA},
\texttt{W1REJ}
\texttt{W1WER},
\texttt{WA1RCQ},
\texttt{WI1Y},
\texttt{WK1H}

\subsection{Guests \& Visitors}
\texttt{NE1O},
Christopher Wentworth

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item The October secretary's report was approved by voice vote.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item The October treasurer's report was approved by voice vote.
\end{enumerate}

\subsubsection{October 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,080.50} \\
  Income: Deposit & \texttt{+\$611.00} \\
  Expense: Equipment & \texttt{-\$169.95} \\
  Expense: Liability Insurance & \texttt{-\$200.00} \\
  Expense: Membership Badges & \texttt{-\$50.81} \\
  Ending Checking Balance & \texttt{\$5,270.74} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$10,038.52} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item We currently have 203 members on the list, there are eight people without a call.
  \item Mark (\texttt{W1IDE}) has an update on the roster that he will share during ``Old Business''.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Greg (\texttt{WA1JXR}) and Mike (\texttt{W1BNC}) are trying to meet with Eric, with the intention on checking out the repeater before the snow flies.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report regarding the 2018 Field Day.
  \item Gerry (\texttt{W1GD}) mentioned that the figures for Field Day were available in the on-line edition of QST for December 2017. We listed as \#9 in Class 6A, which is one better than from \#10 in 2016. Good job everyone!
\end{enumerate}

\section{Old Business}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) began some work on the club roster by migrating it into Google Sheets (Google Docs). This offers a handful of nice benefits.
  \begin{enumerate}
    \item It will make sharing easier. We can share a `Read-Only' link to folks in the Membership Committee and they can see the \emph{always up to date} membership list.
    \item It now pulls information out of the FCC database (Using \texttt{https://callook.info}). This allows us to know when addresses change and callsigns change.
    \item It adds some nice sanity checking to prevent typos. Users no longer need to put addresses in, and it will highlight errors (when names don't match).
    \item Allows us to quickly inspect FCC license validity.
    \item We can run some neat metrics on the club data (How many General / Technician / Extra / Advanced).
    \item It's also pretty.
  \end{enumerate}
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA!
\begin{enumerate}
  \item Donald LaCroix (\texttt{AA1FE}) was voted into CMARA by voice vote. Welcome to the club, we hope to see you at the next meeting!
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item Being November, we had our last session of nominations.
  \begin{enumerate}
  \item The nominations are currently as follow:\\
    \begin{tabular}{|l|l|l|l|}
      \hline
      \textbf{Position}  & \textbf{Number Seats} & \textbf{Name}     & \textbf{Callsign} \\ \hline
      President          & One                   & Bob Peloquin      & \texttt{KB1VUA}   \\ \hline
      Vice President     & One                   & Brian Loverro     & \texttt{K1BML}    \\ \hline
      Secretary          & One                   & Mark Ide          & \texttt{W1IDE}    \\ \hline
      Treasurer          & One                   & Herbert Gilbert   & \texttt{KC1GIB}   \\
                         &                       & Randy Dore        & \texttt{W4FEB}    \\ \hline
      Webmaster          & One                   & Lyn Glagowski     & \texttt{WB1CCL}   \\ \hline
      Board of Directors & Six                   & Adrian Zeffert    & \texttt{AB2IX}    \\
                         &                       & George Gumbrell   & \texttt{KA3RLZ}   \\
                         &                       & Greg Algieri      & \texttt{WA1JXR}   \\
                         &                       & Scott Olsen       & \texttt{KB1EZF}   \\
                         &                       & Dan Rau           & \texttt{K1RAU}    \\
                         &                       & Terry Glagowski   & \texttt{W1TR}     \\ \hline

    \end{tabular}
    \item Terry (\texttt{W1TR}) offered to step down if we had more than six nominations, to allow for `new blood' to get into the board.
    \item Nominations are now closed. Elections will be held in the December meeting.
    \item At this time, the only position running with opposition is the position of Treasurer.
    \item Mark (\texttt{W1IDE}) will be drafting a ballot and sending that to the board members shortly.
  \end{enumerate}

  \item Mark (\texttt{W1IDE}) will be sending out the food sign-ups (for the potluck) just like last year.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item There were no new hams present this month.
  \item We'd like to welcome James McCandless (\texttt{KC1IHO}) back into the hobby after taking 45 years off. He previously was licensed in Puerto Rico.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item No one needs an antenna party.
  \item Greg (\texttt{WA1JXR}) has the MCW project's missing capacitor for everyone. Please reach out to him to obtain that.
  \item Greg (\texttt{WA1JXR}) proposes starting the CW training net on the repeater after the holiday sometime.
  \item The next hamfest is in January 2018 in Whitman, MA.
  \item Adrian (\texttt{AB2IX}) will be retiring and his last day is the same as our potluck in December. We'll have a small celebration for him.
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, December 21, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item This will be our annual potluck, the food sign-ups will be sent out soon.
  \item There was an email sent to the club that may have caused confusion. We are still having the meeting on the third Thursday of December.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned November 16, 2017 at 7:19 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
We had a great presentation by Bruce (\texttt{K1BG}) on the ``Entry Class License'' and how it's been increasingly difficult to get youth into the amateur radio hobby. A big `thank you' goes out to Bruce for helping shed some light on how the FCC has changed the licenses over the last years.

\end{document}
