\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge September 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA September 2017 business meeting was called to order on September 21, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:07 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No  \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & No  \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AE1DX},
\texttt{K1RAU},
\texttt{K1YYT},
\texttt{KA1AQP},
\texttt{KA3RLZ},
\texttt{KB1VXY},
\texttt{KC1ETB},
\texttt{KC1GIB},
\texttt{KM1D},
\texttt{N1FF},
\texttt{N1FSK},
\texttt{N1KWX},
\texttt{W1AHM},
\texttt{W1BNC},
\texttt{W1CAB},
\texttt{W1DYQ},
\texttt{W1GD},
\texttt{W1IKE},
\texttt{W1PA},
\texttt{W1REJ},
\texttt{W1WER},
\texttt{WA1RCQ},
\texttt{WI1Y}

\subsection{Guests \& Visitors}

\texttt{AB1ZW},
\texttt{AC1CO*},
\texttt{KC1IDO*},
\texttt{N1AVP},
Christopher Wentworth

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item The July meeting minutes (the board meeting) was summarized by Mark (\texttt{W1IDE}) and accepted as read by voice vote.
  \item The June meeting minutes were were accepted as published by voice vote.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item The May, June and July summaries were read by Jim (\texttt{N1EKO}) and accepted by voice vote.
  \item The August summary will be tabled until next month.
  \item The ``Radio Donation Sales'' Sub-Account has been folded into the General Club Account.
\end{enumerate}

\subsubsection{May 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,899.20} \\
  Income: Membership Dues & \texttt{+\$270.00} \\
  Expense: Radio \& Other & \texttt{-\$507.98} \\
  Expense: Membership Badges & \texttt{-\$29.56} \\
  Expense: Meeting Location Donation & \texttt{-\$300.00} \\
  Ending Checking Balance & \texttt{\$5,331.66} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$10,099.44} \\
  \hline
\end{tabular}

\subsubsection{June 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,331.66} \\
  Income: Membership Dues & \texttt{+\$256.00} \\
  Expense: Field Day (Misc) & \texttt{-\$134.37} \\
  Expense: Membership Badges & \texttt{-\$29.56} \\
  Ending Checking Balance & \texttt{\$5,453.29} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$10,221.07} \\
  \hline
\end{tabular}

\subsubsection{July 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,453.29} \\
  Income: Membership Dues & \texttt{+\$20.00} \\
  Expense: Field Day (Misc) & \texttt{-\$402.99} \\
  Expense: USPS Postage & \texttt{-\$9.80} \\
  Ending Checking Balance & \texttt{\$5,060.50} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$9,828.28} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item The membership committee needs a copy of the membership, and Jim (\texttt{N1EKO}) will email those to Dick (\texttt{W1REJ}).
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Mike (\texttt{W1BNC}) had a chat with Kurt, and the same topic came up, along with the same promises. Kurt is a busy guy and we recognize that, so we'll be ready when he is.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Gerry (\texttt{W1GD}) ended up getting sick right before field day, but he feels that we did pretty good.
  \item We did get slightly fewer points than in 2016.
  \item Bob's (\texttt{KB1VUA}) motor-home is working, but it's not yet at 100\%. The generator isn't starting yet, so that's still a task.
  \item Bob (\texttt{KB1VUA}) took a moment to apologize for the ticks at field day and informed the club that the site has been spraying in order to reduce the counts going forward.
  \item Bob (\texttt{KB1VUA}) also informed the club that the Astronomy Club has constructed a new building for storage (14' by 20' shed) that may be of use during the next field day.
\end{enumerate}

\section{Old Business}
No business was tabled for discussion this month.

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA!
\begin{enumerate}
  \item George (Andy) Boughton (\texttt{KC1DMM}) was voted in by voice vote.
  \item Ronald Rothman (\texttt{AC1CO}) was voted in by voice vote.
  \item Mark Buonomo (\texttt{KC1IDO}) was voted in by voice vote.
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item During the October and November meetings, well be holding nominations for officer positions and the board of directors.
  \begin{enumerate}
    \item We want to avoid what happened last year, where none of the incumbent members were on the ballot (because of communications regarding nominations). This year, All incumbent officers and directors will automatically be nominated if they wish to run again. All officers will be asked if they wish to run again.
    \item The entire slate will need voting, and while incumbent members may run again, they are not given any preferential treatment in regards to voting.
    \item If you wish to run for a position, please be sure you get a nomination during the next meetings. If you're unable to attend the meetings, please contact a club officer and inform them of your intent to run.
    \item Voting will occur during the December meeting.
  \end{enumerate}
  \item The fine folks over at DX Engineering (\texttt{www.dxengineering.com}) sent the club a letter sharing their interest in giving a presentation at an upcoming meeting. The presentation would be given over Skype and last 30-45 minutes. Topics include DX Engineering, The \texttt{K3LR} Story, Contesting and Contest University, or something customized.
  \begin{enumerate}
    \item Mark (\texttt{W1IDE}) will be reaching out to find out what their schedule looks like and if anything aligns with our availability.
  \end{enumerate}
  \item Ms. Mary Prince reached out to the club regarding the donation of two desks that her husband, Roger Prince (\texttt{W1BR}), used to hold his equipment. They are hoping to donate the desks to someone who would benefit, perhaps someone just getting started in the hobby.
  \begin{enumerate}
    \item Mark (\texttt{W1IDE}) will take the task to follow up with Mary and find out if the desks are still available and if so, see if there are pictures.
    \item Mary did note that she tried to email the club at (\texttt{info@cmara.org}) and she did not get a reply, thus the letter.
  \end{enumerate}
  \item On the topic of field day food, we may attempt to make it more of potluck-style going forward. That would lighten the load on an individual (or group) and allow for more diversity in dishes. Many people brought food to the recent field day and that helped distribute the load. Jim (\texttt{N1EKO}) reports this may have been one of the cheapest (food-wise) field days we've had in some time.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item Mark (\texttt{KC1IDO}) just obtained his technician license. Good work, Mark!
  \item Doug (\texttt{KC1ICX}) also just obtained his technician license. Very nice, welcome to the hobby.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item No one needs an antenna party.
  \item It brings sorrow to the club to hear that we had an operator become a silent key over the summer. Peter (Pete) Dolloff (\texttt{KB1OCF}) of Hudson passed away. Please keep him and his family in your thoughts.
  \item There is a new group based in Ayer for ham radio and electronics hobbyists. Check out \emph{Dan's Tech Night}, run by Dan Pedtke (\texttt{KW2T}). The group meets the second Thursday of the month from 7-10 at the Grady Research Building in Ayer, MA. For more information, visit \texttt{danstechnight.com}.
  \item NEAR-Fest is coming up again, being run this year on October 13 and 14. For more information, visit \texttt{www.near-fest.com}.
  \item The Framingham Amateur Radio Association (FARA) is holding their next monthly meeting (on the first Thursday of the month) and their topic will be on Cold War Rapid CW Operations. The presenter is still working on getting NSA \emph{(Yes, The National Security Agency)} clearance for all the topics. This should be very interesting!
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, October 19, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned September 21, 2017 at 7:43 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
\begin{enumerate}
  \item Greg (\texttt{WA1JXR}) gave a great presentation on soldering. The club then began a hands-on project to assemble their MCW (Modulated CW) circuits. With a lot of beginners soldering for the first time, it was really great to have experienced folks there to help. A big thanks to Greg and all who taught others!
\end{enumerate}

\end{document}
