\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge May 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA Mary 2017 board meeting was called to order on May 18, 2017 at 8:45 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & No \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & No \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\emph{(None)}

\subsection{Guests \& Visitors}
\emph{(None)}

\section{Primary Discussion}

\subsection{Club Projector / Presentations}
\begin{enumerate}
\item Bob (\texttt{KB1VUA}) bought the new projector for the club and it was used tonight. It easily out performed it's predecessor.
\item Jim (\texttt{N1EKO}) has a PA (public announcement) system with a microphone for use during our future presentations.
\end{enumerate}

\subsection{Field Day}
\begin{enumerate}
  \item Rick (\texttt{KA1AQP}) will be doing SDR (software defined radio) in his TV van. He has requested help from Terry (\texttt{W1TR}) to figure out \texttt{N1MM+}.
  \item We need CAT / COM (rig control) on ALL radios being used for field day. \texttt{N1MM+} will then prevent two people from being on the same frequency.
  \item Generators will need to be figured out before field day. Each generator needs a ground rod (connected to the ground terminal). This will ensure we minimize noise on-air.
  \item We still need an owner of field-day power operations.
  \item The discussions on the porta-potty will be tabled until the next meeting.
\end{enumerate}

\section{Next Month's Presentation}
Next month's presentation will be an open discussion on Field Day planning.

\section{Meeting Adjourned}
The meeting was adjourned May 18, 2017 at 9:03 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
