\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge February 2017 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA February 2017 business meeting was called to order on February 16, 2017 by CMARA president Bob Peloquin (\texttt{KB1VUA}) at 7:17 PM.

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & Yes \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & Yes \\
  Randy Dore        & \texttt{W4FEB}    & Yes \\
  Johnathan Sherman & \texttt{WW2JS}    & No  \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{AB1ZW},
\texttt{K1RAU},
\texttt{KA1AQP},
\texttt{KB1EZF},
\texttt{KB1QZD},
\texttt{KB1VXH},
\texttt{KB1VXY},
\texttt{KC1BHD},
\texttt{KC1GBK},
\texttt{KC1GIB},
\texttt{KM1D},
\texttt{N1FSK},
\texttt{N1HTB},
\texttt{W1AHM},
\texttt{W1BNC},
\texttt{W1CAB},
\texttt{W1IKE},
\texttt{W1PA},
\texttt{WA1MDD},
\texttt{WA1RCQ}

\subsection{Guests \& Visitors}
\texttt{KA1SPY}*,
\texttt{KB2SAE},
\texttt{KC1DMM},
\texttt{KC1EKJ}*,
\texttt{KC1GYT},
\texttt{W1DYQ},
\texttt{W1GJM},
Christopher Wentworth\\

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
The secretary's reports for both December 2016 and January 2017 were voted in by verbal vote.

\newpage
\subsection{Treasurer's Report}
The January 2017 treasurer's report was voted in via verbal vote.

\subsubsection{January 2017 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$4,835.83} \\
  Income: Membership Dues & \texttt{+\$673.00} \\
  Expense: Membership Badges & \texttt{-\$13.63} \\
  Expense: Office Supplies & \texttt{-\$46.25} \\
  Ending Checking Balance & \texttt{\$5,448.95} \\
  \hline
  \hline
  CD & \texttt{\$4,767.78} \\
  \hline
  \hline
  Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
  \hline
  \hline
  Radio Donation Sales & \texttt{\$1,268.04} \\
  \hline
  \hline
  \textbf{Total Club Account} (Checking + CD) & \texttt{\$10,216.73} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
Nothing to report.

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Most of the repeater trustees met in the last week, and discussed future plans for the CMARA repeater.
  \item Of the hardware that is available, the Yaesu DR2 and a Bitcom repeater seem like some of the better options. There is a high concern about duty-cycle and the Yaesu promises a 50 Watt, 100\% duty-cycle operation, and the Bitcom is focused on commercial use.
  \item Greg (\texttt{WA1JXR}) shared his reservations about running at the duty-cycle that the repeater is rated for. It's better to run under the rated wattage to lengthen the lifetime of the unit. To help this, we can use an external amplifier to supplement the power.
  \item Our current repeater is rated for 100 watts, but is only running at around 40 watts.
  \item Question to Greg (\texttt{WA1JXR}): Should we replace the amplifier or repeater first? Answer: Unfortunately, the way that the current system is constructed, the swap needs to occur all at once.
  \item Mike (\texttt{W1BNC}) had a discussion with Kurt regarding our antenna. Kurt has some antennas and is fine with moving things around for us. He needs to wait until spring and he will likely be a bit busy because of new channel changes.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report.
  \item Bob (\texttt{KB1VUA}) is looking for people who are interested in forming this year's field day committee. Volunteers were: Adrian (\texttt{AB2IX}) and John (\texttt{WA1MDD}). If you're interested, please reach out to Bob (\texttt{KB1VUA}).
\end{enumerate}

\section{Old Business}
\begin{enumerate}
  \item The December 2016 secretary was voted in during the Secretary's report section.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
\begin{enumerate}
  \item Jack Kenney (\texttt{KA1SPY}) was voted in by majority vote. Welcome to CMARA!
  \item Morris Beverly (\texttt{KC1EKJ}) was voted in by majority vote. Welcome to CMARA!
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item Herb (\texttt{KC1GIB}) spoke with Bob (\texttt{KB1VUA}) regarding the struggles that can occur with George's Old Timer's Net. Specifically, there is a difficult problem of seeking substitute net control operators. Herb has become the George's Old Timer's Net Coordinator with approval from the club and Bob (\texttt{KB1VUA}).
  \begin{enumerate}
    \item It's important to note that GOTN is a community driven net, but since CMARA does operate the repeater the net runs on, it's good to seek approval.
    \item We need to get some of Herb's contact information on the \texttt{www.cmara.org} website. Mark (\texttt{W1IDE}) will reach out to Lyn (\texttt{WB1CCL}) to get it up there.
  \end{enumerate}
  \item Mark (\texttt{W1IDE}) has spent some time over the last months making various CMARA documents available as open source resources.
  \begin{enumerate}
    \item This serves a few major purposes. Firstly, the meeting minutes and note templates are now available for others to download and reference.
    \item Secondly, this enables version control which allows us to track specific changes. This allows for members to see how meeting minutes change over time.
    \item The new GitHub repository (and related Travis CI build) serve as a point of reference for folks to find ``the'' latest copy of any given notes.
    \item If you're interested in checking out the files (or becoming a contributor), check out\\ \texttt{https://github.com/cmara} or reach out to Mark (\texttt{W1IDE}).
    \item Mark (\texttt{W1IDE}) will reach out to Lyn (\texttt{WB1CCL}) to get a link onto the website.
  \end{enumerate}
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item Jack (\texttt{KA1SPY}) recently got his original call back as a vanity. Glad to hear you could get it, Jack!
  \item Mike (\texttt{KC1GYT}) has recently joined the ham radio community. Welcome, we're sure you'll enjoy it!
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item Greg (\texttt{WA1JXR}) provided an update on the club Modulated CW (MCW) project. He has developed the printed circuit board (PCB) design. The kit will be a great project for all skill levels, as it's completely through-hole (no surface mount soldering). At this point, the project looks like about \$10 for the PCB and about \$30 for the parts (for a total of about \$40). Greg will reach out to folks again to make sure he has everyone interested. If you're interested, please reach out to Greg at \texttt{wa1jxr@comcast.net}.
  \item This Saturday (February 18, 2017) will be the annual Algonquin ARC Ham Radio Flea Market. It will be held at the Marlborough 1st Lt. Charles W. Whitcomb School (formerly known as the Marlborough Intermediate/Middle School). For more information, check out their website at\\ \texttt{http://www.qsl.net/n1em/}.
  \item The Framingham ARA Spring Flea Market will be held this year on April 23, 2017 at the Keefe Technical School. For more information, check out \texttt{http://w1fy.org/flea.aspx}.
  \item The board has discussed the value of snacks at our meetings, and thusly the board members will take turns bringing edibles to the meetings.
\end{enumerate}

\section{Next Meeting}
The next meeting will be Thursday, March 16, 2017 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.\\

\noindent
The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.\\

\noindent
The topic of the next meeting will be decided during the board meeting following the conclusion of the business meeting.

\section{Meeting Adjourned}
The meeting was adjourned February 16, 2017 at 7:53 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
Sandy (\texttt{N1FSK}) gave a great presentation on CMARA history. Sandy has been working on gathering and writing documentation about the club history and this is the first presentation of his findings. We owe Sandy a big ``thank you'' for gathering all this and sharing it with the club, its really wonderful to have this on record. A copy of the presentation can be found at the following link:\\

\noindent
\texttt{http://cmara.org/about/history/201702-cmara-history-presentation.pdf}

\end{document}
