\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge September 2017 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA September 2017 board meeting was called to order on September 21, 2017 at 9:15 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Jim Singer     & \texttt{N1EKO}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert    & \texttt{AB2IX}    & Yes \\
  Harold Carlson    & \texttt{N1ZC}     & No  \\
  Greg Algieri      & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski   & \texttt{W1TR}     & No  \\
  Randy Dore        & \texttt{W4FEB}    & No  \\
  Johnathan Sherman & \texttt{WW2JS}    & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KC1GIB}, \texttt{W1PA}

\subsection{Guests \& Visitors}
Christopher Wentworth

\section{Primary Discussion}

\subsection{Channel 5 Studio Tour with Mike (\texttt{W1BNC})}
\begin{enumerate}
  \item Mike (\texttt{W1BNC}) has offered to make a group visit/tour to the Channel 5 station in Needham.
  \item Part of Mike's motivation is that his is considering retirement soon and this would obviously need to be done before that.
  \item The tour would consist of at least the studio and control room.
  \item It was discussed if we'd use this as a meeting ``presentation'' or if it'd be better as a separate meetup. We would rather have it not be the meeting, so that timing can be easier for folks.
  \item Mark (\texttt{W1IDE}) will email the club with a poll to find out how many people are interested in this tour.
\end{enumerate}

\subsection{Summer Board Meeting}
While the food was a little eclectic, it was very valuable to have a board meeting between the regular sessions.

\subsection{Field Day}
We will not have any field day results until November or October, as the results won't be published until then.

\subsection{General Meeting Topic Ideas}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) will send DX Engineering an email about upcoming meeting schedules and see what they had in mind regarding presentations. This was a continuation regarding the letter from DX Engineering sent to CMARA which was discussed during the business meeting earlier in the night.
  \item Greg (\texttt{WA1JXR}) knows someone who gave a presentation regarding the new FCC licenses. Greg will take the task of reaching out to that person to find out if he'd be willing to present to CMARA.
  \item A presentation on foxhunting (signal searching) could be really interesting. We don't know anyone who can give this presentation.
  \item The continuation of the club MCW project; we don't want to use the same topic too often, but at the same time there are quite a few people that didn't finish.
  \item Perhaps a combined meeting session, with various different breakout sessions after the business meeting. This is an idea we could do as a workshop.
  \item There is nothing wrong with just a plain-old social meeting, in the name of networking.
  \item Mark (\texttt{W1IDE}) will send a poll to the club to find out what members would be interested in seeing during the presentation.
\end{enumerate}

\subsection{Projector Screen}
Our normal projector screen is nowhere to be found. Bob (\texttt{KB1VUA}) has left a note for the pastor, to see if they've seen it.

\subsection{Church's Electrical Work}
The church has not responded to our offer to help with the various electrical work.

\section{Next Month's Presentation}
Next month's presentation will be determined by board members leading up to the meeting.

\section{Meeting Adjourned}
The meeting was adjourned September 21, 2017 at 9:40 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
