\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge June 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA June 2018 business meeting was called to order on June 21, 2018 by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{W1TAB}    & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No  \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & No  \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & No  \\
  George Gumbrell & \texttt{KA3RLZ}   & Yes \\
  L. Greg Algieri & \texttt{WA1JXR}   & No  \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & No  \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{KA1AQP},
\texttt{KB1VXY},
\texttt{KC1GIB},
\texttt{N1AZL},
\texttt{N1EKO},
\texttt{N1TJC},
\texttt{W1AHM},
\texttt{W1CAB},
\texttt{W1LB},
\texttt{W1REJ},
\texttt{WA1MDD},
\texttt{WW2JS}

\subsection{Guests \& Visitors}
\emph{(None)}

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
CMARA Secretary (Mark, \texttt{W1IDE}) was not able to attend this meeting due to a work emergency. No minutes were voted in.

\newpage
\subsection{Treasurer's Report}
The summary of May's treasurer's report was read by Randy (\texttt{W4FEB}). The report was accepted as read by voice vote.

\subsubsection{May 2018 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$6265.30} \\
  Expense: Badges & \texttt{-\$6.25} \\
  Ending Checking Balance & \texttt{\$6259.05} \\
  \hline
  \hline
  LCU Certificate of Deposit & \texttt{\$4,825.32} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$11,084.37} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\emph{(No notes taken)}

\subsubsection{Repeater Trustees Report}
\emph{(No notes taken)}

\subsubsection{Field Day Committee Report}
\emph{(No notes taken)}

\section{Unfinished Business}
\emph{(No notes taken)}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
% There were no new CMARA members voted in this month.
We would like to welcome the following members to CMARA! All members were voted in by voice vote.
\begin{enumerate}
  \item \texttt{KC1HSC}, Frank
  \item \texttt{W1IPI}, Alan
  \item \texttt{W1MYS}, Patrick
  \item \texttt{WA1HZN}, Jeff
  \item \texttt{W1FSH}, William
  \item \texttt{N1TJC}, Tom
  \item \texttt{KC1JCB}, John
\end{enumerate}

\subsection{Other New Business}
\emph{(No notes taken)}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\emph{(No notes taken)}

\subsection{Other News}
\emph{(No notes taken)}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be September 16. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned June 21, 2018 by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Post-Meeting Presentation}
\emph{(No notes taken)}

\end{document}
