\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge May 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA May 2018 business meeting was called to order on May 17, 2018 at 7:11 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{W1TAB}    & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & Yes \\
  George Gumbrell & \texttt{KA3RLZ}   & Yes \\
  L. Greg Algieri & \texttt{WA1JXR}   & No  \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & No  \\
  \hline
\end{tabular}

\subsection{Members Present}
\texttt{K1TIN},
\texttt{K1YYT},
\texttt{KA1AQP},
\texttt{KC1FPI},
\texttt{KC1IOK},
\texttt{KC1SDL},
\texttt{KC1SGT},
\texttt{KM1D},
\texttt{N1EKO},
\texttt{N1FSK},
\texttt{N1TQ},
\texttt{N1ZC},
\texttt{NE1D},
\texttt{NE1R},
\texttt{W1CAB},
\texttt{W1DYQ},
\texttt{W1GD},
\texttt{W1IDE},
\texttt{W1JKS},
\texttt{W1REJ},
\texttt{W1TAB},
\texttt{WA1RCQ},
\texttt{WI1Y},
\texttt{WW2JS},
\texttt{WZ1Z}

\subsection{Guests \& Visitors}
Rebecca Ide

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item As Mark (\texttt{W1IDE}) was absent last month (April), we need to discuss and vote on March's meeting minutes. The minutes were distributed via email to the membership and accepted as published by voice vote.
  \item The April meeting minutes were distributed by email to the membership and they were approved as published by voice vote.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
The summary of April's treasurer's report was read by Randy (\texttt{W4FEB}). The report was accepted as read by voice vote.

\subsubsection{April 2018 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$6089.30} \\
  Income: Dues Collected & \texttt{+\$160.00} \\
  Income: Equipment Sale & \texttt{+\$167.00} \\
  Expense: Badges & \texttt{-\$15.00} \\
  Expense: PO Box Rental & \texttt{-\$136.00} \\
  Ending Checking Balance & \texttt{\$6265.30} \\
  \hline
  \hline
  LCU Certificate of Deposit & \texttt{\$4,825.32} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$11,090.62} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item The FCC is reporting that the number of people who are upgrading from General to Extra is decreasing. It's questioned if the difference between the classes is too minor, or if this is an effect of interest falling off.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Mike (\texttt{W1BNC}) recapped the events of last month's amplifier failure.
  \item The Repeater Trustees are still looking for another amplifier so we can return the one that's running now.
  \item There is also a serious desire to build up a spare set of equipment. Mike (\texttt{W1BNC}) mentioned that it can be difficult to test individual components of a system like this, and that a complete spare may be easier to test.
  \item If anyone has a Micor (or really any) repeater that the club could make use of, please reach out to Mike (\texttt{W1BNC}).
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Field day is June 24 and 25 this year. and we'll be operating out of the `Aldrich Astronomical Society, Inc.' field.
  \item We are still looking for a coordinator for power.
  \item Harold (\texttt{N1ZC}) has volunteered to be the coordinator for networking.
  \item We still have positions open for station operators, station chairs, and relief operators. Please reach out to Gerry (\texttt{W1GD}) if you're interested, regardless of your experience level.
  \item Gerry (\texttt{W1GD}) would like to see GOTA (\emph{Get-On-The-Air}) stations running at night to give less experienced folks an opportunity to operate.
  \item Next meeting (June 21) will be the annual N1MM training held by Terry (\texttt{W1TR}).
\end{enumerate}

\section{Unfinished Business}
\begin{enumerate}
  \item We needed to discuss and vote in the March meeting minutes, and that was completed during the secretary's report section.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
There were no new CMARA members voted in this month.
% We would like to welcome the following members to CMARA! All members were voted in by voice vote.
% \begin{enumerate}
%   \item \texttt{KC1HSC}, Frank
% \end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item The next meeting is Thursday, and Field day starts Saturday, so you may want to make sure you're packed.
  \item Dan (\texttt{K1RAU}) will be coordinating the food for field day this year, but he is looking and welcoming of any help that can be found. Please reach out to him; his email can be found on QRZ.
  \item Dan (\texttt{K1RAU}) also mentioned the importance of having red flashlights when operating at field day, especially when the astronomy club is present. We also need to consider vehicle lights and have them pointed away from the group.
  \item Bob (\texttt{W1TAB}) has also approved us to have a campfire.
  \item Bob (\texttt{W1TAB}) mentioned that weather permitting, the astronomy club may have their telescopes out for our enjoyment.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item Bob (\texttt{W1TAB}) has acquired a new vanity call \texttt{W1TAB} as a switch from his original \texttt{KB1VUA}. This is a direct reference to his recent purchase of a Tab Trailer.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item Last month's swap meet was a great success. Not only did our membership get good deals on new equipment, but the club made a few dollars from donations. We'd like to give a huge `Thank You' to Adrian (\texttt{AB2IX}) for coordinating all the details.
\end{enumerate}


\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be TBD. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item The next meeting's topic will be the annual \texttt{N1MM} training for field day, held by Terry (\texttt{W1TR}).
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned March 15, 2018 at 7:51 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Post-Meeting Presentation}
Thanks to Terry (\texttt{W1TR}) for sharing his experience making a pneumatic antenna launcher.

\end{document}
