\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge May 2018 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Notes by Dan Rau (\texttt{K1RAU}), prepared by Mark Ide (\texttt{W1IDE}), Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA May 2018 board meeting was called to order on May 17, 2018 at 8:56 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{W1TAB}    & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}   & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    &  Yes \\ \hline
  George Gumbrell & \texttt{KA3RLZ}   &  Yes \\ \hline
  L. Greg Algieri & \texttt{WA1JXR}   &  No  \\ \hline
  Terry Glagowski & \texttt{W1TR}     &  Yes \\ \hline
  Dan Rau         & \texttt{K1RAU}    &  Yes \\ \hline
  Scott Olsen     & \texttt{KB1EZF}   &  Yes \\ \hline
\end{tabular}\\

\subsection{Members Present}
\texttt{WI1Y}, \texttt{WW2JS}

\subsection{Guests \& Visitors}
\emph{(None)}

\section{Primary Discussions}

\subsection{Summer Board Meeting}
There is a summer board meeting planned for Saturday, September 8 at Dan Rau's (\texttt{K1RAU}) home. It will be held at 8PM.

\subsection{Next Month's Snacks}
Mark (\texttt{W1IDE}) has offered to bring the snacks for the June meeting.

\subsection{Membership Poll}
Mark (\texttt{W1IDE}) will issue a poll to the club (or find the results from the previous).

\subsection{September Presentation}
We have a couple potential presentations for September.
\begin{enumerate}
  \item Dan (\texttt{KW2T}), from Dan's Tech Night, may have a presentation to give. Dant (\texttt{K1RAU}) will email for follow up.
  \item Bob (\texttt{W1TAB}) may have a presentation on Solar.
\end{enumerate}

\section{Next Month's Presentation}
Terry (\texttt{W1TR}) will present the \texttt{N1MM} training in preperation for field day.

\section{Meeting Adjourned}
The meeting was adjourned May 17, 2018 at 9:11 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\end{document}
