\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge April 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA April 2018 business meeting was called to order on April 19, 2018 at 7:15 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No  \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & Yes \\
  George Gumbrell & \texttt{KA3RLZ}   & No  \\
  L. Greg Algieri & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & No  \\
  \hline
\end{tabular}

\subsection{Members Present}
\begin{enumerate}
\item \texttt{K1TIN}, Ameena Jabbour
\item \texttt{KB1JUG}, Teresa Vanfechtmann
\item \texttt{KC1DMM}, George Boughton
\item \texttt{KC1IOK}, Douglas Macaloney
\item \texttt{KC1IUS},  Bruce de Graaf
\item \texttt{KC1SDL}, Selina Lovett
\item \texttt{KM1D}, Raymond Donadt
\item \texttt{N1FSK}, Sandy Lancraft
\item \texttt{N1KWX}, Eugene Bouchard
\item \texttt{NE1D}, Dimitris Paliyannis
\item \texttt{NE1R}, Thomas Carrigan
\item \texttt{W1AHM}, Alan Martin
\item \texttt{W1CAB}, Craig Bolen
\item \texttt{W1GD}, Gerald Kersus
\item \texttt{W1GJM}, Gary McMeekin
\item \texttt{W1REJ}, Richard Jubinville
\item \texttt{WA1MDD}, John Spencer
\item \texttt{WA1RCQ}, Arthur Kass
\item \texttt{WI1Y}, Milton Westover
\item \texttt{WW2JS}, Jonathan Sherman
\end{enumerate}

\subsection{Guests \& Visitors}
\begin{enumerate}
  \item \texttt{KC1HSC}, Francis Bock\textasteriskcentered{}
  \item \texttt{KA1AQP}, Richard Kenadek
\end{enumerate}

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) is not present, so the meeting minutes will not be voted in.
  \item Brian (\texttt{K1BML}) took notes for Mark.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item Approved as read.
\end{enumerate}

% \subsubsection{January 2018 Treasurer's Summary}
% \noindent
% \begin{tabular}{|l|r|}
%   \hline
%   Beginning Checking Balance & \texttt{\$5,315.87} \\
%   Income: Dues Collected & \texttt{+\$540.00} \\
%   Expense: \emph{None} & \texttt{-\$0.00} \\
%   Ending Checking Balance & \texttt{\$5,855.87} \\
%   \hline
%   \hline
%   LCU Certificate of Deposit & \texttt{\$4,825.32} \\
%   \hline
%   \hline
%   \textbf{Total Club Account} & \texttt{\$10,681.19} \\
%   \hline
% \end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item The ham radio hobby is growing.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Mike (\texttt{W1BNC}) reported that the \texttt{W1BIM} repeater has been operating at a reduced 10 watts due to a problem with the amplifier.
  \item Greg (\texttt{WA1JXR}) and Mike (\texttt{W1BNC}) put the public service band amplifier to replace the amplifier that failed.
  \item Mike (\texttt{W1BNC}) has had some offers for amplifiers.
  \item Currently the club does not have any spare amplifiers.
  \item Greg (\texttt{WA1JXR}) will come up with a proposal and a replacement plan.
  \item Mike (\texttt{W1BNC}) will also have a report for the next meeting in May.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Field day is June 24 and 25 this year.
  \item We'll be operating out of the `Aldrich Astronomical Society, Inc.' as we have in the previous years.
  \item We are looking for a coordinator for power.
  \item We do not have a count of how many stations we'll operate.
  \item We do not have plans for networking. We need someone to lead the effort there.
  \item Mark (\texttt{W1IDE}) will send out a sign up sheet via email.
\end{enumerate}

\section{Unfinished Business}
\emph{(None)}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA! All members were voted in by voice vote.
\begin{enumerate}
  \item \texttt{KC1HSC}, Frank
\end{enumerate}

\subsection{Other New Business}
\emph{(None)}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\emph{(None)}

\subsection{Other News}
\begin{enumerate}
  \item Dick (\texttt{W1REJ}) built up a tower and it's working great.
  \item Selina (\texttt{KC1SDL}) shared that there is an event coming up on May 12, experience Ham Radio. It's held at Annie's Bookstop in Worcester, 65 James Street. For more details check out the event's Facebook page: \\ \texttt{https://www.facebook.com/events/426327701139451/}
  \item John (\texttt{WA1MDD}) shared there is a antique car show coming up and they're looking for some help with a two-meter simplex net. Please email John at \texttt{jwspencer@msn.com}.
  \item Nearfest is May 4 and 5 this year.
  \item Eastern CT Amateur Radio Club is holding a flea at Thompson Speedway CT. April 29, 2018.
\end{enumerate}


\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, May 17th, 2018 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item The next meeting's topic will be a members-only flea. See the minutes above for more details.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned March 15, 2018 at 7:58 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
Thanks to Adrian (\texttt{AB2IX}) for putting together the flea tonight.

\end{document}
