\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge February 2018 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA February 2018 board meeting was called to order on February 15, 2018 by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes  \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}   & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    &  Yes \\ \hline
  George Gumbrell & \texttt{KA3RLZ}   &  Yes \\ \hline
  L. Greg Algieri & \texttt{WA1JXR}   &  Yes \\ \hline
  Terry Glagowski & \texttt{W1TR}     &  Yes \\ \hline
  Dan Rau         & \texttt{K1RAU}    &  Yes \\ \hline
  Scott Olsen     & \texttt{KB1EZF}   &  Yes \\ \hline
\end{tabular}\\

\subsection{Members Present}

\begin{tabular}{|l|l|}
\hline
\textbf{Name} & \textbf{Callsign} \\ \hline
Jonathan Sherman & \texttt{WW2JS} \\ \hline
Craig Brauckmiller & \texttt{KC1ETB} \\ \hline
\end{tabular}

\subsection{Guests \& Visitors}
\emph{(None)}

\section{Primary Discussion}

\subsection{March Presentation}
Sandy (\texttt{N1FSK}) and Tom (\texttt{N1TQ}) will talk about their SDR mcHF homebrew Project.  Bob (\texttt{KB1VUA}) and Brian (\texttt{K1BML}) will contact them for more details.

\subsection{April Presentation}
The April ``presentation'' will be a club flea market / equipment swap. There will need to be better control and monitoring of the sales because last year’s goal of each seller giving a small portion of the proceeds to the club fizzled out.

\subsection{May Meeting}
For the May meeting, the following topics may need to be covered:
\begin{enumerate}
\item Pre-Field day discussion
\item Committee reports
\item Coordination of committees to provide equipment, services, catering and general well being.
\end{enumerate}

\subsection{June Presentation}
In June, Terry (\texttt{W1TR}) will give the \texttt{N1MM} training needed for field day.

\subsection{General}
There was an idea shared that field day should be mentioned in some capacity during each business meeting, in order to keep the ball rolling.

\subsection{Potential Repeater Upgrade}
\begin{enumerate}
\item Greg (\texttt{WA1JXR}) will get with the other trustees and discuss the upgrade requirements.
\item Any antenna work has to be done in conjunction with other tower work.
\item Terry (\texttt{W1TR}) suggested Bruce Marcus because he is a Hytera dealer.
\item There was some lively discussion about who would initiate any repeater upgrades.
\item The Trustees can recommend and advise and execute and the club (by vote) provides the funds.
\end{enumerate}

\section{Next Month's Presentation}
The next meeting is March 15th, 2018. See `March Presentation' above for the presentation goals.

\section{Meeting Adjourned}
The meeting was adjourned February 15, 2018 at 9:15 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
