\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge August 2018 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Notes by Dan Rau (\texttt{K1RAU}), prepared by Mark Ide (\texttt{W1IDE}), Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA August 2018 board meeting was called to order on August 21, 2018 at 6:55 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).\\

This meeting was \textbf{NOT} held on the standard third-Thursday. This was held on August 21, 2018 at Dan Rau's home.

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{W1TAB}    & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & No  \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No  \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & No  \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}   & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    &  Yes \\ \hline
  George Gumbrell & \texttt{KA3RLZ}   &  Yes \\ \hline
  L. Greg Algieri & \texttt{WA1JXR}   &  Yes \\ \hline
  Terry Glagowski & \texttt{W1TR}     &  No  \\ \hline
  Dan Rau         & \texttt{K1RAU}    &  Yes \\ \hline
  Scott Olsen     & \texttt{KB1EZF}   &  No  \\ \hline
\end{tabular}\\

% \subsection{Members Present}
% \texttt{WI1Y}, \texttt{WW2JS}

\subsection{Guests \& Visitors}
\begin{enumerate}
  \item Patrick Faucher
  \item Herb Gilbert (\texttt{KC1GIB})
  \item Chris Wentworth
\end{enumerate}

\section{Primary Discussions}

\subsection{Planning for 2018/2019 Season}
\begin{itemize}
\item \textbf{September:}\\
Dan Pedtke on Impedance.
\item \textbf{October:}\\
Bob Peloquin on Inverter Generators
\item \textbf{November:}\\
Arian Zeffert on 3-D printers.
Nominations for officers.
\item \textbf{December:}\\
Christmas Party\\
Election of officers
\item \textbf{January:}\\
Open
\item \textbf{February:}\\
Open
\item \textbf{March:}\\
Mickey Westover on building an off-center diapole.
\item \textbf{April:}\\
Adrian Zeffert and the Club Swap Meet to benefit new hams
\item \textbf{May:}\\
Field Day Planning
\item \textbf{June:}\\
N1MM training for Field Day.
\end{itemize}

\subsection{Other Business}
Greg Algeri brought info from the trustees about the repeater equipment situation. The trustees will be ready to make a recommendation either in the September or October meeting.\\

\noindent
Preliminary cost estimates for repeater controller, preamp, amp and antenna would be between 3 and 4k. Greg feels that unless we resolve the transmit antenna issue soon a good fix for the transmit coverage is a 200 amplifier running at 100 watts. That should restore the transmit coverage to roughly the same contour as the receive coverage. There is now internet at the W1BIM site which could allow us to have telemetry and full multiple access remote control.

\section{Next Month's Presentation}
Dan Pedtke on Impedance

\section{Meeting Adjourned}
The meeting was adjourned August 21, 2018 at 8:00 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\end{document}
