\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge January 2018 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA January 2018 board meeting was called to order on January 18, 2018 at 7:38 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes  \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}   & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    &  Yes \\ \hline
  George Gumbrell & \texttt{KA3RLZ}   &  Yes \\ \hline
  L. Greg Algieri & \texttt{WA1JXR}   &  Yes \\ \hline
  Terry Glagowski & \texttt{W1TR}     &  No  \\ \hline
  Dan Rau         & \texttt{K1RAU}    &  Yes \\ \hline
  Scott Olsen     & \texttt{KB1EZF}   &  No  \\ \hline
\end{tabular}\\

\subsection{Members Present}
\emph{(None)}

\subsection{Guests \& Visitors}
\emph{(None)}

\section{Primary Discussion}

\subsection{Robert's Rules}
\begin{enumerate}
  \item Going forward efforts will be made to hold our meetings in accordance with Robert's Rules of Parliamentary Procedure. In the past we've been relaxed, but after some issues with elections and member feedback, we'll get back on track.
  \item Mark (\texttt{W1IDE}) is taking the action to study Robert's Rules and report back with findings that the club could implement.
\end{enumerate}

\subsection{Event of Ties}
\begin{enumerate}
  \item During the December election, the question came up about how to handle ties. In the moment, we didn't know the answer and we should find out.
  \item Mark (\texttt{W1IDE}) is taking the action (above) to study Robert's Rules and will report back with how to handle a tie. If it is unclear, or unsatisfactory we may need to modify the By-Laws to include procedure.
\end{enumerate}

\subsection{Field Day 2018}
\begin{enumerate}
  \item Field Day will be held at the astronomy club (unless something changes).
  \item There will be no motor-home this year from Bob (\texttt{KB1VUA}).
\end{enumerate}

\subsection{Swap Meet}
\begin{enumerate}
  \item Adrian (\texttt{AB2IX}) suggested a Swap Meet when the weather gets warmer. The Board agreed to consider and check the calendar for a likely date.
\end{enumerate}

\subsection{Letter for Randy}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) needs to get Randy (\texttt{W4FEB}) a letter for each bank and account stating he is now the new Treasurer.
  \item Randy (\texttt{W4FEB}) will provide Mark (\texttt{W1IDE}) with the account numbers and banks we have accounts at.
\end{enumerate}

\section{Next Month's Presentation}
The next meeting is February 15th, 2018. The board will discuss options for the content of the meeting via email over the next weeks.

\section{Meeting Adjourned}
The meeting was adjourned in an unofficial fashion due to the Skype presentation starting. Any topics that were not covered will need to be brought up at next month's meeting or via email.

\end{document}
