\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge March 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2018 business meeting was called to order on March 15, 2018 at 7:00 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & Yes \\
  George Gumbrell & \texttt{KA3RLZ}   & Yes \\
  L. Greg Algieri & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\begin{enumerate}
\item \texttt{AC1EH}, Jon Goguen
\item \texttt{K1YYT}, Gerard Bachand
\item \texttt{KA1AQP}, Richard Kenadek
\item \texttt{KB1LOU}, Ronald Diprofio
\item \texttt{KB1SCD}, Stephen Daukas
\item \texttt{KB1VXH}, George Saari
\item \texttt{KC1DMM}, George Boughton
\item \texttt{KC1ETB}, Craig Brauckmiller
\item \texttt{KC1HSC}, Francis Bock
\item \texttt{KC1IOK}, Douglas Macaloney
\item \texttt{KC1ITY}, Thomas Levergood
\item \texttt{KM1D}, Raymond Donadt
\item \texttt{N1EKO}, James Singer
\item \texttt{N1FSK}, Sandy Lancraft
\item \texttt{N1HTB}, Dimitris Paliyannis
\item \texttt{N1TQ}, Thomas Qualtieri
\item \texttt{N1ZC}, Harold Carlson, Jr.
\item \texttt{W1AHM}, Alan Martin
\item \texttt{W1CAB}, Craig Bolen
\item \texttt{W1GD}, Gerald Kersus
\item \texttt{W1PA}, William Acito, Jr.
\item \texttt{W1REJ}, Richard Jubinville
\item \texttt{W1WER}, James Young
\item \texttt{WA1RCQ}, Arthur Kass
\item \texttt{WI1Y}, Milton Westover
\item \texttt{WW2JS}, Jonathan Sherman
\item \texttt{WZ1Z}, Patrick Faucher, Jr.
\end{enumerate}

\subsection{Guests \& Visitors}
\begin{enumerate}
\item Samantha Harris, Daughter of Adrian (\texttt{AB2IX})
\item TBD, waiting on updated membership list.
\end{enumerate}

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) emailed the membership the meeting minutes, but since it was last minute he summarized during the meeting. The minutes were approved by voice vote.
  \item There was one typo correction `Roger's Rules' should have been `Robert's Rules'.
  \item There was a suggestion to specifically call out for new hams; that may help get a better representation of upgrades.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item The January treasurer's report has an error and Randy (\texttt{W4FEB}) corrected it.  See the summary below for the correct January summary.
  \item The February treasurer's report was read by Randy (\texttt{W4FEB}) and was approved by voice vote.
  \item Randy (\texttt{W4FEB}) reported on the breakdown of the club's accounts and what amounts are present in each.
\end{enumerate}

\subsubsection{January 2018 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,315.87} \\
  Income: Dues Collected & \texttt{+\$540.00} \\
  Expense: \emph{None} & \texttt{-\$0.00} \\
  Ending Checking Balance & \texttt{\$5,855.87} \\
  \hline
  \hline
  LCU Certificate of Deposit & \texttt{\$4,825.32} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$10,681.19} \\
  \hline
\end{tabular}

\subsubsection{February 2018 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,855.87} \\
  Income: Dues Collected (Meeting) & \texttt{+\$210.00} \\
  Income: Dues Collected (PO Box) & \texttt{+\$47.00} \\
  Income: Badge Fees & \texttt{+\$7.00} \\
  Expense: Ordered Checks & \texttt{-\$54.07} \\
  Ending Checking Balance & \texttt{\$6065.80} \\
  \hline
  \hline
  LCU Certificate of Deposit & \texttt{\$4,825.32} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$10,891.00} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item We've increased by five members since the last time the report was given. We are not sure of where the members heard of the club.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Nothing to report.
  \item As a reminder, the club is isolated from the repeater trustees. The by-laws allow the repeater trustees to operate independently, and bring their suggestions to the board. Neither the board nor the club has the ability to instruct the repeater trustees to perform any actions.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report.
  \item Gerry (\texttt{W1GD}) will bring a report with the needed leadership positions next month, and we'll try to get those seats filled.
\end{enumerate}

\section{Unfinished Business}
\begin{enumerate}
  \item Randy (\texttt{W4FEB}) reported on the breakdown of the club accounts during the treasurer's report.
  \item Mark (\texttt{W1IDE}) has been sitting on the task to create club QSL cards for some time. The pricing is about \$15 for 100, or \$60 for 1,000 (the more you order, the lower the unit cost). Mark will mock up some designs for the club and will bring them to the board in April. All purchases are tabled until after we get a design. It's proposed that 100-200 is likely plenty to order.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA! All members were voted in by voice vote.
\begin{enumerate}
  \item \texttt{AC1EH}, Jon Goguen\\ Jon found the club via the \texttt{CM2M} net; he got a piece of traffic and came to a meeting.
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item April's Ham Flea Meet
  \begin{enumerate}
    \item Adrian (\texttt{AB2IX}) will be running a club ham flea meet.
    \item The last swap meet was chaotic to say the least, so this time will have more structure.
    \item If you are looking to sell during the meet, you'll be required to cover your items until it's time to sell. Likewise, there are little tickets to help keep track of club donations.
    \item We're asking for 5\% club donations on any sale to help cover our costs. It's only \$0.50 on a \$10 sale; we're not really asking for a lot.
    \item This will be for members only, so please pay your dues before April, or you won't be a member!
  \end{enumerate}
  \item Please be sure to pay your club dues at the next meeting! We appreciate your support and you'll lose membership privileges if you fail to pay after some time.
  \item It would help us run the meeting if only one person speaks at a time. We've found many side conversations tend to occur during the business meeting and it makes it both hard to run the meeting and for others to hear. Please try to keep your side conversations to a minimum until after the business meeting.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item We welcome Jon (\texttt{AC1EH}) back to the hobby after abouts 50 years! So while not \emph{technically} a new ham, it's a new call.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item Adrian (\texttt{AB2IX}) brought a box of spare parts. If you look in and see something you could use, it's yours. Anyone is welcome to take any of the parts at no cost.
  \item There was an open question about the status of membership cards (the business cards we get to confirm our membership each year). Randy (\texttt{W4FEB}) has a stack from folks that haven't picked them up yet, so go see him after the meeting.
  \item Andy (\texttt{KC1DMM}) brought some fliers for the Framingham Flea market on April 8, 2018 at Keefe Technical High School. Be sure to check it out! For more information, checkout \texttt{fara.org/flea}.
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, April 19th, 2018 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item The next meeting's topic will be a members-only flea. See the minutes above for more details.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned March 15, 2018 at 7:55 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
Our post-meeting presentation was a great presentation by Sandy (\texttt{N1FSK}) and Tom (\texttt{N1TQ}) shared a great presentation on their mcHF kit project: `A Journey to the Edge of Ham Radio'. Thank you Sandy and Tom!

\end{document}
