\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge October 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA June 2018 business meeting was called to order on October 18, 2018 at 7:06 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{W1TAB}    & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & No  \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & Yes \\
  George Gumbrell & \texttt{KA3RLZ}   & Yes \\
  L. Greg Algieri & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & Yes \\
  \hline
\end{tabular}

\subsection{Attendance}

\texttt{AB1ZW},
\texttt{AB2IX},
\texttt{K1CCS},
\texttt{K1RAU},
\texttt{K1SAC},
\texttt{K1VEA},
\texttt{K1YYT},
\texttt{KA1YOO},
\texttt{KA3RLZ},
\texttt{KB1EZF},
\texttt{KB1NIP},
\texttt{KB1VXY},
\texttt{KB1YLA},
\texttt{KC1BHD},
\texttt{KC1ETB},
\texttt{KC1GIB},
\texttt{KC1IOK},
\texttt{KC1JCB},
\texttt{KC1SDL},
\texttt{KM1D},
\texttt{N1EFR},
\texttt{N1EKO},
\texttt{N1GEX},
\texttt{N1IEX},
\texttt{N1ZC},
\texttt{NE1O},
\texttt{W1AHM},
\texttt{W1GD},
\texttt{W1IDE},
\texttt{W1LB},
\texttt{W1LEB},
\texttt{W1PA},
\texttt{W1RAU},
\texttt{W1REJ},
\texttt{W1TAB},
\texttt{W1TR},
\texttt{W4FEB},
\texttt{WA1JXR},
\texttt{WA1MDD},
\texttt{WA1RCQ},
\texttt{WK1H},
\texttt{WW2JS},
Chris Wentworth,
Rebecca Ide

% \subsection{Guests \& Visitors}
% \emph{(None)}

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
CMARA Secretary (Mark, \texttt{W1IDE}) is waiting for the minutes from September's meeting. At this time, there were no minutes to present.

\newpage
\subsection{Treasurer's Report}
CMARA Treasurer (Randy, \texttt{W4FEB}) accidentally forgot the report at home and was unable to present. Report tabled until next month.
% The summary of May's treasurer's report was read by Randy (\texttt{W4FEB}). The report was accepted as read by voice vote.

% \subsubsection{May 2018 Treasurer's Summary}
% \noindent
% \begin{tabular}{|l|r|}
%   \hline
%   Beginning Checking Balance & \texttt{\$6265.30} \\
%   Expense: Badges & \texttt{-\$6.25} \\
%   Ending Checking Balance & \texttt{\$6259.05} \\
%   \hline
%   \hline
%   LCU Certificate of Deposit & \texttt{\$4,825.32} \\
%   \hline
%   \hline
%   \textbf{Total Club Account} & \texttt{\$11,084.37} \\
%   \hline
% \end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
CMARA has 207 known members, only 92 of which are paid. The remaining have lapsed or left the club. Nationally, the hobby has approximately 248,000 members.

\subsubsection{Repeater Trustees Report}
The CMARA repeater trustees (\texttt{WA1JXR}, \texttt{W1EPH}, \texttt{N1VX}, and \texttt{W1BNC}) prepared a presentation regarding a potential repeater upgrade. The report was extremely detailed and the general summary is as follows: \\

\noindent
\begin{tabular}{|l|r|}
\hline
\textbf{Component} & \textbf{Cost} \\ \hline
Repeater & \texttt{\$2000} \\
Controller & \texttt{\$500} \\
Amplifier & \texttt{\$1300} \\
Power Supply & \texttt{\$500} \\
Isolator & \texttt{\$500} \\ \hline
\textbf{Total} & \texttt{\$4800} \\ \hline
\end{tabular}

\subsubsection{Field Day Committee Report}
There was nothing to report for field day.

\section{Unfinished Business}
There was no known unfinished business.

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
% There were no new CMARA members voted in this month.
We would like to welcome the following members to CMARA! All members were voted in by voice vote.
\begin{enumerate}
  \item Christopher Wentworth \emph{(Not yet a ham, but wants to support CMARA)}
  \item \texttt{K1DX} George Woods
\end{enumerate}

\subsection{Other New Business}

\begin{enumerate}
  \item We had the first of our board and officer nominations. If you would like to run for any position, you still can. Let someone know before or during the November meeting. Nominations are listed below.\\

  \begin{tabular}{|ll|ll|}
    \hline
    \textbf{Position} & \textbf{Seats} & \textbf{Nominee} & \textbf{Call} \\ \hline
    President & 1 & Bob Peloquin & \texttt{W1TAB} \\ \hline
    Vice President & 1 & \emph{(None)} & \\ \hline
    Secretary & 1 & \emph{(None)} & \\ \hline
    Treasurer & 1 & Randolph Dore & \texttt{W4FEB} \\ \hline
    Webmaster & 1 & Lyn Glagowski & \texttt{WB1CCL} \\ \hline
    Board of Directors & 6 & Adrian Zeffert & \texttt{AB2IX} \\
    & & George Gumbrell& \texttt{KA3RLZ} \\
    & & L. Greg Algieri & \texttt{WA1JXR} \\
    & & Terry Glagowski & \texttt{W1TR} \\
    & & Dan Rau & \texttt{K1RAU} \\
    & & Scott Olsen & \texttt{KB1EZF} \\
    & & Albert Hayeck & \texttt{N1EFR} \\ \hline
  \end{tabular}

  \item In order to be overly verbose and clear, the following statements are true regarding the nominations.
  \begin{enumerate}
    \item Bob Peloquin (\texttt{W1TAB}) has been nominated for the position of club president.
    \item There has been no nomination for the position of vice president, but incombent Brian Loverro (\texttt{K1BML}) has not been asked if he'd like a nomination. The intention is to ask him in the November meeting.
    \item There has been no nomination for the position of secretary. Mark Ide (\texttt{W1IDE}) has voiced that he's unable to balance his increased workload and family time with the club's needs.
    \item Randolph Dore (\texttt{W4FEB}) has been nominated for the position of club treasurer.
    \item Lyn Glagowski (\texttt{WB1CCL}) has been nominated for the position of webmaster. Her husband, Terry (\texttt{W1TR}) accepted her nomination for her.
    \item Several people have been nominated for the board of directors (they will be listed below). Since there are more than six nominees, you only the six with the highest number of votes will be elected.
    \item Adrian Zeffert (\texttt{AB2IX}) has been nominated for a seat on the board.
    \item George Gumbrell (\texttt{KA3RLZ}) has been nominated for a seat on the board.
    \item L. Greg Algieri (\texttt{WA1JXR}) has been nominated for a seat on the board.
    \item Terry Glagowski (\texttt{W1TR}) has been nominated for a seat on the board. Terry has shared he is willing to step down in order to share the board and club with new interested members.
    \item Dan Rau (\texttt{K1RAU}) has been nominated for a seat on the board.
    \item Scott Olsen (\texttt{KB1EZF}) has been nominated for a seat on the board.
    \item Albert Hayeck (\texttt{N1EFR}) has been nominated for a seat on the board.
    \item We will have another round of nominations in November. If you're intested in running for any position, please let someone know who can nominate you, or if you'll be ther, you can nominate yourself.
    \item Anyone can run for any position.
    \item In December, people can continue to run as a Write-In.
    \item It is our intention that prior to the ballots being issued in the December meeting, every nominated candidate will be able to respond to any quetions and/or statements and be able to give a final word prior to votes being cast.

  \end{enumerate}
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
There we no new hams nor upgrades.

\subsection{Other News}
\begin{enumerate}
  \item We'd like to thank Dan Pedtke (\texttt{KW2T}) for his wonderful presentation last month.
  \item Mark Richards (\texttt{K1MGY}) is always looking for volunteers for all sorts of events. Volunteering as an operator is a great way to give back to the community. Reach out to Mark if you find yourself with some extra time and you'd like to help out. Thanks to Dan (\texttt{K1RAU}) for bringing this news to the club.
  \item Selina (\texttt{KC1SDL}) is looking to have an antenna party on October 28 around 1PM. Dan (\texttt{K1RAU}) is helping to organize this and can be reached via email if you're able to help.
  \item The Nutmeg Hamfest in Meriden CT is on October 21st. It's approximately 75 miles from Worcester, MA. Visit \texttt{nutmeghamfest.com} for more details.
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be November 15, 2018. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned October 10, 2018 by CMARA president Bob Peloquin (\texttt{W1TAB}) at approximately 7:28 PM.

\section{Post-Meeting Presentation}
\emph{(No notes taken)}

\end{document}
