\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{\texttt{https://github.com/mide/cmara-meeting-minutes/}}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge December 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Notes by Brian \texttt{K1BML} Vice President, prepared by Mark \texttt{W1IDE} Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA December 2018 business meeting was called to order on December 20, 2018 at 7:00 PM by CMARA president Bob Peloquin (\texttt{W1TAB}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{W1TAB}    & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & No  \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & Yes \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & No  \\
  George Gumbrell & \texttt{KA3RLZ}   & No  \\
  L. Greg Algieri & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & No  \\
  \hline
\end{tabular}

\subsection{Attendance}

\texttt{K1BML},
\texttt{K1CAB},
\texttt{K1RAU},
\texttt{KB1VXY},
\texttt{KC1ETB},
\texttt{KC1FPI},
\texttt{KC1GIB},
\texttt{KC1IOK},
\texttt{KC1SGT},
\texttt{N1EFR},
\texttt{N1EKO},
\texttt{N1FSK},
\texttt{N1KWX},
\texttt{W1AHM},
\texttt{W1BNC},
\texttt{W1REJ},
\texttt{W1SS},
\texttt{W1TAB},
\texttt{W1TR},
\texttt{W4FEB},
\texttt{WA1JXR},
\texttt{WB1CCL},
\texttt{WZ1Z}

% \subsection{Guests \& Visitors}
% \emph{(None)}

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
No report.

\newpage
\subsection{Treasurer's Report}
No report.

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
No report.

\subsubsection{Repeater Trustees Report}
No report.

\subsubsection{Field Day Committee Report}
No report.

\section{Unfinished Business}
There was no known unfinished business.

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
There were no new CMARA members voted in this month.


\subsection{Other New Business}

\begin{enumerate}
  \item Bob (\texttt{W1TAB}) explained the election process.
  \item The club voted to suspend Roberts Rules in order to proceed with elections.
  \item Nominations were opened for the second in-person meeting. Only the following nominations are valid. All incumbent officers and directors have been nominated.

  \begin{tabular}{|ll|lll|}
    \hline
    \textbf{Position} & \textbf{Seats} & \textbf{Nominee} & \textbf{Call} & \textbf{Incumbent} \\ \hline
    President & 1 & Bob Peloquin & \texttt{W1TAB} & Yes \\
     &  & Brian Loverro & \texttt{K1BML} & \\ \hline
    Vice President & 1 & Brian Loverro & \texttt{K1BML} & Yes \\
     &  & James Singer & \texttt{N1EKO} & \\ \hline
    Secretary & 1 & Mark Ide & \texttt{W1IDE} & Yes \\
     & & Dan Rau & \texttt{K1RAU} &  \\ \hline
    Treasurer & 1 & Randolph Dore & \texttt{W4FEB} & Yes \\ \hline
    Webmaster & 1 & Lyn Glagowski & \texttt{WB1CCL} & Yes \\ \hline

    Board of Directors & 6 & Adrian Zeffert & \texttt{AB2IX} & Yes\\
    & & George Gumbrell& \texttt{KA3RLZ} & Yes \\
    & & L. Greg Algieri & \texttt{WA1JXR} & Yes \\
    & & Terry Glagowski & \texttt{W1TR} & Yes \\
    & & Dan Rau & \texttt{K1RAU} & Yes \\
    & & Scott Olsen & \texttt{KB1EZF} & Yes \\
    & & Herbert Gilbert & \texttt{KC1GIB}& \\
    & & Albert Hayeck & \texttt{N1EFR}& \\ \hline
  \end{tabular}
  \item Nominations have been closed. At this time, no additional nominations will be accepted.

\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
There we no new hams nor upgrades.

\subsection{Other News}
No other news.

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be January 17, 2019. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned December 20, 2018 by CMARA president Bob Peloquin (\texttt{W1TAB}) at approximately 7:15 PM.

\section{Post-Meeting Presentation}
\emph{(No notes taken)}

\end{document}
