\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge January 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA January 2018 business meeting was called to order on January 18, 2018 at 7:13 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes  \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    &  Yes \\ \hline
  George Gumbrell & \texttt{KA3RLZ}   &  Yes \\ \hline
  L. Greg Algieri & \texttt{WA1JXR}   &  Yes \\ \hline
  Terry Glagowski & \texttt{W1TR}     &  No  \\ \hline
  Dan Rau         & \texttt{K1RAU}    &  Yes \\ \hline
  Scott Olsen     & \texttt{KB1EZF}   &  No  \\ \hline
  \hline
\end{tabular}

\subsection{Members Present}
\begin{enumerate}
\item \texttt{AB2IX}, Adrian Zeffert
\item \texttt{K1BML}, Brian Loverro
\item \texttt{K1RAU}, Dan Rau
\item \texttt{K1YYT}, Gerard Bachand
\item \texttt{KA3RLZ}, George Gumbrell
\item \texttt{KB1JUG}, Teresa Vanfechtmann
\item \texttt{KB1VUA}, Robert Peloquin, Jr.
\item \texttt{KB1VXH}, George Saari
\item \texttt{KB1VXY}, John Iwuc
\item \texttt{KC1DMM}, G. Andy Boughton
\item \texttt{KC1DTT}, Michael Latour
\item \texttt{KC1DYA}, Kevin Romines
\item \texttt{KC1ETB}, Craig Brauckmiller
\item \texttt{KC1GIB}, Herbert Gilbert
\item \texttt{KC1IOK}, Douglas Macaloney
\item \texttt{KC1SDL}, Selina Lovett
\item \texttt{KE3KK}, Ronald Rothman
\item \texttt{KM1D}, Raymond Donadt
\item \texttt{KW2T}, Daniel Pedtke
\item \texttt{N1EKO}, James Singer
\item \texttt{N1HTB}, Dimitris Paliyannis
\item \texttt{W1AHM}, Alan Martin
\item \texttt{W1CAB}, Craig Bolen
\item \texttt{W1DYQ}, Dean Huggins
\item \texttt{W1GD}, Gerald Kersus
\item \texttt{W1IDE}, Mark Ide, Jr.
\item \texttt{W1REJ}, Richard Jubinville
\item \texttt{W1WER}, James Young
\item \texttt{W4FEB}, Randolph Dore
\item \texttt{WA1JXR}, L. Greg Algieri
\item \texttt{WZ1Z}, Patrick Faucher, Jr.
\end{enumerate}

\subsection{Guests \& Visitors}

% \noindent
% \textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item The December secretary's report was approved by voice vote as published. There were no corrections.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item The December treasurer's report was approved by voice vote as read by Jim (\texttt{N1EKO}). There were no corrections nor concerns.
  \item The 2018 annual report was approved by voice vote as read by Jim (\texttt{N1EKO}). There were no corrections nor concerns.
\end{enumerate}

\subsubsection{October 2017 Treasurer's Summary}
\noindent
\emph{Pending getting November summary.}
% \begin{tabular}{|l|r|}
%   \hline
%   Beginning Checking Balance & \texttt{\$5,080.50} \\
%   Income: Deposit & \texttt{+\$611.00} \\
%   Expense: Equipment & \texttt{-\$169.95} \\
%   Expense: Liability Insurance & \texttt{-\$200.00} \\
%   Expense: Membership Badges & \texttt{-\$50.81} \\
%   Ending Checking Balance & \texttt{\$5,270.74} \\
%   \hline
%   \hline
%   CD & \texttt{\$4,767.78} \\
%   \hline
%   \hline
%   Repeater Fund (Maintain minimum \$500 in checking) & \texttt{\$910.00} \\
%   \hline
%   \hline
%   \textbf{Total Club Account} & \texttt{\$10,038.52} \\
%   \hline
% \end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report.
  \item Bob (\texttt{KB1VUA}) noted that we will have more members on the committee this year, so that it's less load on each.
\end{enumerate}

\section{Old Business}
\begin{enumerate}
  \item Mark (\texttt{W1IDE}) read the outcome of December's election.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA!
\begin{enumerate}
  \item John Barbato (\texttt{N2LND}) is welcomed into CMARA. Upon inspection of our membership list, John may have already been a member. The final motion was `John will be a new member or renewed if already a member'.
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item Please be sure to pay your club dues at the next meeting! We appreciate your support and with our new attempt at following Roger's Rules, you'll lose membership privileges if you fail to pay after some time.
  \item Greg (\texttt{WA1JXR}) has started the Monday night `Learn CW' net. It replaces the time slot of George's Old Timer's Net. On the first night there were 37 check-ins. Thanks to Greg for running this!
  \item We will be making more of an effort to abide by Robert's Rules during our meetings. This is a learning process for many of us, so we do ask everyone for patience during this process. Thanks!
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item Bruce got his callsign \texttt{KC1IUS}. Congratulations!
  \item Patrick got his new callsign \texttt{WZ1Z}. He was previously \texttt{AE1DX}.
  \item Selina (\texttt{KC1SDL}) upgraded to General. Congratulations!
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item There is an analog / \texttt{C4FM} Yaesu Fusion repeater on \texttt{446.825 MHz}, with a PL of \texttt{100 Hz}.
  \item The Whitman Amateur Radio Club is holding their WinterFest Flea Market this Saturday, January 20, 2018.
  \item Adrian (\texttt{AB2IX}) needs some help hanging an antenna in a 90 foot tree. If you're able to help, please reach out to Adrian and join the antenna party.
  \item Greg (\texttt{WA1JXR}) reminds everyone who assembled the MCW kits that he has your missing resistor if you haven't picked it up yet.
  \item Gil Hayes (\texttt{WK1H}) wanted to share that during one of the larger recent storms, The National Weather Service (NWS) and \texttt{WX1BOX} received 60+ reports from local hams through the \texttt{W1BIM} repeater. They were very happy and thankful for all the local support.
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, February 15, 2018 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item The next meeting's presentation will be determined by the board by email prior to the next email.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned January 18, 2018 at 7:31 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
We had a Skype (remote) presentation by Bob Naumann (\texttt{W5OV}) on the DX Engineering Story. We thank Bob and DX Engineering for joining us this month.

\end{document}
