\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

% Put watermark on
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft}
% \SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge March 2018 Board of Directors Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA March 2018 board meeting was called to order on March 15, 2018 at 8:57 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}   & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    &  Yes \\ \hline
  George Gumbrell & \texttt{KA3RLZ}   &  Yes \\ \hline
  L. Greg Algieri & \texttt{WA1JXR}   &  Yes \\ \hline
  Terry Glagowski & \texttt{W1TR}     &  Yes \\ \hline
  Dan Rau         & \texttt{K1RAU}    &  Yes \\ \hline
  Scott Olsen     & \texttt{KB1EZF}   &  Yes \\ \hline
\end{tabular}\\

\subsection{Members Present}
\emph{(None)}

\subsection{Guests \& Visitors}
\emph{(None)}

\section{Primary Discussion}

\subsection{This Month's (March) Presentation}
Sandy (\texttt{N1FSK}) and Tom (\texttt{N1TQ}) gave a truly fantastic presentation on their SDR mcHF homebrew Project. Almost everyone was engaged and many asked questions. The loudspeakers helped a lot, and we may need to use those in the future.


\subsection{Field Day}
\subsubsection{Food}
Dan (\texttt{K1RUA}) has stepped up to provide food services for field day. He will reach out to Art (\texttt{WA1RCQ}) for help as Art has done this before. We still need to obtain grills and other things, like tables and tents.

\subsection{Club Snacks}
George (\texttt{KA3RLZ}) brought the snacks this month, and Dan (\texttt{K1RAU}) has offered to bring them next month.

\subsection{CMARA Website}
\subsubsection{Renewal Fees}
Terry (\texttt{W1TR}) brought up for Lyn (\texttt{WB1CCL}) that she needs approval to renew the website. The cost will be about \$100.00. Bob (\texttt{KB1VUA}) will follow up as the board believes this already was approved during the December meeting. No new approval was granted.

\subsubsection{Disappointment with Late Email}
Terry (\texttt{W1TR}) voiced his disappointment about the monthly email not going out with sufficient time to update the website, it was only sent a day and a half prior to the meeting and that was not fair to Lyn. Mark (\texttt{W1IDE}) agreed and will work harder to be more punctual with the emails going out in the future.\\

\noindent
The board did recall that at the end of the February board meeting, the presentation was already established and did not change.

\subsection{Disaster Recovery Plan for Repeater}
George (\texttt{KA3RLZ}) asked for a disaster recovery (DR) plan in the event something happens to our existing repeater. This is simply a written analysis of what hardware we'd likely need to replace and if ``instant replacement'' of that hardware is worth the cost. The hope is to have the plan by September.

\subsection{Bill (\texttt{KC5SPF})'s Equipment}
Greg (\texttt{WA1JXR}) received some surplus equipment from Bill (\texttt{KC5SPF}) and discussed with the board how to handle the donation. Given the upcoming sale, the equipment will be placed on a ``CMARA'' table, where 100\% of the sale price goes to the club. It's also a possibility we auction it off, but we don't know the exact mechanics of the sales yet.\\

\noindent
\begin{tabular}{|p{5in}|l|}
\hline
\textbf{Description} & \textbf{Model Number} \\ \hline
Vectronics Manual Antenna Tuner 1000W Roller Inductor tuner with Cross Needle Meter built in and LED PEP Power Meter & HTF-1500 \\ \hline
MFJ Econo Tuner Manual Antenna no meter & MFJ-900 \\ \hline
GC Electronics HF SWR Meter & \emph{no model number} \\ \hline
Radio Shack SWR/Power Meter 20/200/2KW Avg/PEP & 21-524 \\ \hline
Radio Shack Micronta 13.8V @ 1.75A Power Supply & 22-127D \\ \hline
\end{tabular}

\subsection{Church Donation}
Randy (\texttt{W4FEB}) has given a check of \$300.00 to the church for allowing us to use their space.

\section{Next Month's Presentation}
The April ``presentation'' will be a club flea market / equipment swap. Adrian (\texttt{AB2IX}) will be taking the lead and will be working with Mark (\texttt{W1IDE}) with communications about this.

\section{Meeting Adjourned}
The meeting was adjourned March 15, 2018 at 9:15 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\end{document}
