\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\pagestyle{fancyplain}

% Put watermark on
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{7}

\lhead{}
\chead{Central Massachusetts Amateur Radio Association}
\rhead{}
\lfoot{}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\begin{document}

\begin{center}
{\huge February 2018 Business Meeting}\\
\emph{of the}\\
{\Large Central Massachusetts Amateur Radio Association}\\
\emph{Submitted by Mark Ide \texttt{W1IDE}, Secretary}
\end{center}

\section{Meeting Called to Order}
The CMARA February 2018 business meeting was called to order on February 15, 2018 at 7:00 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Attendance}
\noindent
Below is the list of members and guests that attended the meeting. If you are not caught up on your dues, you'll be listed as a guest. If you feel that's in error, please reach out the club treasurer.

\subsection{Officers Present}
\begin{tabular}{|l|l|l|c|}
  \hline
  \textbf{Position} & \textbf{Name}  & \textbf{Callsign} & \textbf{Present} \\ \hline
  President         & Bob Peloquin   & \texttt{KB1VUA}   & Yes \\
  Vice President    & Brian Loverro  & \texttt{K1BML}    & Yes \\
  Secretary         & Mark Ide       & \texttt{W1IDE}    & Yes \\
  Treasurer         & Randolph Dore  & \texttt{W4FEB}    & Yes \\
  Webmaster         & Lyn Glagowski  & \texttt{WB1CCL}   & No  \\
  \hline
\end{tabular}

\subsection{Board of Directors Present}
\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Name}     & \textbf{Callsign} & \textbf{Present} \\ \hline
  Adrian Zeffert  & \texttt{AB2IX}    & Yes \\
  George Gumbrell & \texttt{KA3RLZ}   & Yes \\
  L. Greg Algieri & \texttt{WA1JXR}   & Yes \\
  Terry Glagowski & \texttt{W1TR}     & Yes \\
  Dan Rau         & \texttt{K1RAU}    & Yes \\
  Scott Olsen     & \texttt{KB1EZF}   & Yes \\
  \hline
\end{tabular}

\subsection{Members Present}
\begin{enumerate}
\item \texttt{AB2IX}, Adrian Zeffert
\item \texttt{K1BML}, Brian Loverro
\item \texttt{K1RAU}, Dan Rau
\item \texttt{KA3RLZ}, George Gumbrel
\item \texttt{KB1EZF}, Scott Olsen
\item \texttt{KB1JUG}, Teresa Vanfechtmann
\item \texttt{KB1VUA}, Bob Peloquin
\item \texttt{KB1VXY}, John Iwuc
\item \texttt{KC1ETB}, Craig Brauckmiller
\item \texttt{W1AHM}, Alan Martin
\item \texttt{W1GD}, Gerald Kersus
\item \texttt{W1IDE}, Mark Ide, Jr.
\item \texttt{W1REJ}, Richard Jubinville
\item \texttt{W1TR}, Terry Glagowski
\item \texttt{W1WER}, James Young
\item \texttt{W4FEB}, Randolph Dore
\item \texttt{WA1JXR}, L. Greg Algieri
\item \texttt{WA1MDD}, John Spencer
\item \texttt{WA1RCQ}, Arthur Kass
\item \texttt{WW2JS}, Jonathan Sherman
\end{enumerate}

\subsection{Guests \& Visitors}
\begin{enumerate}
\item \texttt{KB1LRL}, Ray Lajoie
\item \texttt{KC1IOK}, Douglas Macaloney*
\item \texttt{KC1ITY}, Thomas Levergood*
\item \texttt{KC5SPF}, William Duntzee, III.*
\end{enumerate}

\noindent
\textasteriskcentered{} Entered as a guest. Voted in as new member. See \S{} \ref{new-cmara-members} for details.

\section{Reports}

\subsection{Secretary's Report}
\begin{enumerate}
  \item The January secretary's report stands approved with noted corrections.
\end{enumerate}

\newpage
\subsection{Treasurer's Report}
\begin{enumerate}
  \item The January treasurer's report was approved by voice vote as read by Randy (\texttt{W4FEB}).
  \item There was an open question on the amounts pertaining to the \$510 \texttt{W1BIM} repeater fund; did the numbers include it, or not? Randy (\texttt{W4FEB}) is going to investigate and get back to us.
\end{enumerate}

\subsubsection{January 2018 Treasurer's Summary}
\noindent
\begin{tabular}{|l|r|}
  \hline
  Beginning Checking Balance & \texttt{\$5,315.87} \\
  Income: Dues Collected & \texttt{+\$540.00} \\
  Expense: \emph{None} & \texttt{-\$0.00} \\
  Ending Checking Balance & \texttt{\$5,855.87} \\
  \hline
  \hline
  LCU CD & \texttt{\$4,825.32} \\
  \hline
  \hline
  \textbf{Total Club Account} & \texttt{\$10,681.19} \\
  \hline
\end{tabular}

\subsection{Committee Reports}

\subsubsection{Membership Committee Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\subsubsection{Repeater Trustees Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\subsubsection{Field Day Committee Report}
\begin{enumerate}
  \item Nothing to report.
\end{enumerate}

\section{Unfinished Business}
\begin{enumerate}
  \item No unfinished business.
\end{enumerate}

\section{New Business}

\subsection{New CMARA Members}
\label{new-cmara-members}
We would like to welcome the following members to CMARA! All members were voted in by voice vote.
\begin{enumerate}
  \item \texttt{AB1HO}, Spencer Borden, Jr.
  \item \texttt{KC1IOK}, Douglas Macaloney
  \item \texttt{KC1ITY}, Thomas Levergood
  \item \texttt{KC5SPF}, William Duntzee, III.
  \item \texttt{N1PAZ}, Timothy Huntington
\end{enumerate}

\subsection{Other New Business}
\begin{enumerate}
  \item Please be sure to pay your club dues at the next meeting! We appreciate your support and with our new attempt at following Roger's Rules, you'll lose membership privileges if you fail to pay after some time.
  \item Randy (\texttt{W4FEB}) has confirmed that he has access to the bank accounts. Mark (\texttt{W1IDE}) provided him with an official letter he was able to bring to the locations and obtain access.
\end{enumerate}

\section{For the Good of the Club}

\subsection{New Hams \& Upgrades}
\begin{enumerate}
  \item No new hams nor upgrades present.
\end{enumerate}

\subsection{Other News}
\begin{enumerate}
  \item This meeting was conducted under strict `Robert's Rules' conformity. After about thirty minutes, the consensus of the club is that we know we need some level of formality (especially surrounding things like elections and formal business), but we can still make the club fun by doing things our way. We'll be trying to find the right balance in the upcoming months.
\end{enumerate}

\section{Next Meeting}
\begin{enumerate}
  \item The next meeting will be Thursday, March 15th, 2018 at 7:00 PM. It will be located at the Oakdale United Methodist Church, 15 North Main Street, West Boylston, MA 01583.
  \item The meeting will begin promptly at 7:00 PM. Social time will start around 6:30 PM, so be sure to come early if you would like to mingle.
  \item The next meeting's presentation will be determined by the board by email prior to the next email.
\end{enumerate}

\section{Meeting Adjourned}
The meeting was adjourned February 15, 2018 at 7:31 PM by CMARA president Bob Peloquin (\texttt{KB1VUA}).

\section{Post-Meeting Presentation}
Our post-meeting presentation was another kit-night, led by Greg (\texttt{WA1JXR}). members were welcomed to continue their soldering projects and ask questions.

\end{document}
